---
title: "Make It Personal: Boston Index Preliminary Results"
output: html_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
author:
- Erik Thulin, ethulin@rare.org
- Rakhim Rakhimov, rrakhimov@rare.org
---

```{r setup, include = FALSE, echo = FALSE, results = 'asis'}
library(tidyverse)
library(haven)
library(labelled)
library(data.table)
library(knitr)
library(reactable)
library(htmltools)
library(lubridate)
library(hrbrthemes)
library(survey)
options(scipen = 999)
library(scales)

data <- read_sav("spss_4_17_2021.sav")
lucid_data <-read.csv("lucid_response_4_19_2021.csv")
```

```{r, include = FALSE, echo = FALSE, results = 'asis', eval = FALSE}
# Incompletes match between Lucid and Alchemer
lucid <- read.csv("lucid_data_analysis_4_17_2021.csv")

test <- lucid %>% 
  filter(FulcrumStatus == 3 & ClientStatus == 10 & SupplierName != "Z - Test Supplier") %>% 
  mutate(
    var13 = as.character(Response.ID),
    var13 = tolower(var13))

test_merge <- merge(x = data, y = test, by = "var13", all.x = TRUE)

test_merge <- test_merge %>% 
  select(var13, Response.ID)

test_merge$Response.ID <- as.character(test_merge$Response.ID)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
lucid_data <- lucid_data %>% 
  filter(SupplierName != "Z - Test Supplier") %>% # remove test responses
  select(-HISPANIC.3., -REGION.6., -Ethnicity...Detailed.7.) %>% 
  mutate(
    ID = as.character(Response.ID),
    ID = tolower(ID))

data$ID <- data$var13

data <- merge(x = lucid_data, y = data, by = "ID", all.y = TRUE)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
data <- data %>%
select(-PID, -MID, -RespondentSID, -Response.ID, -IsLive, -Survey.Number, -SurveyName, -STATE.4., -ZIP.2., -Vcid, -Vcomment, -Vlanguage, -Vreferer, -Vsessionid, -Vuseragent, -VGeoCountry, -Vpostal, var10, -var112, -var113, -var10) %>% 
rename(sex = var3,
       age = var2,
       White = var8O33,
       Black = var8O34,
       Native_American = var8O35,
       Asian = var8O36,
       Native_Hawaiian = var8O37,
       Other = var8O38,
       ethnicity = ETHNICITY.8.) %>% 
mutate(sex = case_when(sex == 10003 ~ "Male", TRUE ~ "Female"),
       ethnicity = case_when(Vrid == 394 ~ "White", 
                             Vrid == 1008 ~ "Asian", 
                             Vrid == 184 ~ "White", 
                             Vrid == 1505 ~ "Black", 
                             Vrid == 193 ~ "Black", 
                             TRUE ~ ethnicity),
       ethnicity = case_when(ethnicity == 1 ~ "White", 
                             ethnicity == 2 ~ "Black", 
                             ethnicity == 3 ~ "Alaska_Native", 
                             ethnicity == 4 ~ "Asian", 
                             ethnicity == 5 ~ "Asian", 
                             ethnicity == 6 ~ "Asian", 
                             ethnicity == 7 ~ "Asian", 
                             ethnicity == 8 ~ "Asian", 
                             ethnicity == 9 ~ "Asian", 
                             ethnicity == 10 ~ "Asian", 
                             ethnicity == 15 ~ "Other", 
                             TRUE ~ ethnicity)) %>%
  filter(age >= 18 & age <= 150)
```

```{r, include=FALSE, echo = FALSE, warning = FALSE}
#Demo prop
demo <- read.csv("demo_w.csv")

demo <- demo %>% 
  select(-`ï..demo_combined`) %>% 
  filter(prop > 0) %>% 
  rename(sex = gender,
         pop.demo.prop = prop,
         ethnicity = race)

# Create age brackets
agebreaks <- c(18, 25, 35, 45, 55, 65, 100)
agelabels <- c("18-24", "25-34", "35-44", "45-54", "55-64", "65+")
# Add age brackets to df
setDT(data)[ , age_group := cut(age, 
                                breaks = agebreaks, 
                                right = FALSE, 
                                labels = agelabels)]

data$ethnicity <- as.factor(data$ethnicity)

#Demo sample
#Counting demos in sample
d <- data %>% 
  select(Vrid, sex, age_group, ethnicity)

d <- d %>% 
  group_by(sex, ethnicity, age_group) %>%
  summarise(count=n()) 

d <- d %>% 
  mutate(sample.demo.prop = count/sum(d$count))

#Merging population and sample demos. Demo groups in pop need to be the same as demo groups in sample.

d <- merge(x = d, y = demo, by = c("ethnicity", "age_group", "sex"), all.x = TRUE)

#d <- d %>% 
#  mutate(demo_weight = pop.demo.prop/sample.demo.prop) 

#d <- d %>% select(ethnicity, age_group, sex, demo_weight)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
# ZIP weight population
pop_zip <- read.csv("geocorr_cbsa_zip.csv")

pop_zip <- pop_zip %>% 
  filter(cbsa == "14460") %>% 
  select(-cbsa, -cbsaname15, -zipname)

pop_zip$zip <- as.numeric(as.character(pop_zip$zcta))
pop_zip$zip.pop <- as.numeric(as.character(pop_zip$pop10))
pop_zip$pop.zip.prop <- as.numeric(as.character(pop_zip$afact))

pop_zip <- pop_zip %>% 
  filter(zip < 99999) %>% 
  select(zip, zip.pop, pop.zip.prop)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
#ZIP weight sample
df <- data %>% 
  select(Vrid, var21)
  
df$zip <- as.numeric(as.character(df$var21))
df$ID <- as.numeric(as.character(df$Vrid))

df <- df %>% 
  select(ID, zip)%>% 
  gather(ID, zip) %>% 
  group_by(zip) %>%
  summarise(count=n()) 

df <- df %>% 
  mutate(sample.zip.prop = count/sum(count))

df <- merge(df, pop_zip, by = "zip")

df <- df %>% 
  mutate(zip.weight = pop.zip.prop/sample.zip.prop)

df <- df %>% 
  select(zip, zip.weight)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
### weighting by puma
#population
puma <- read.csv("geocorr_puma_export.csv")

puma <- puma %>% 
  filter(cbsa == "14460") %>% 
  select(PUMAname, pop10) %>% 
  rename(puma = PUMAname,
         puma.pop = pop10)

puma$puma.pop <- as.numeric(as.character(puma$puma.pop))

puma$puma <- as.character(puma$puma)
puma$puma <- as.factor(puma$puma)

puma <- puma %>% 
  mutate(pop.puma.prop = puma.pop/sum(puma.pop))
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
#DF matching ZIPs to PUMAs
zip_puma <- read.csv("geocorr_puma_zip.csv")

zip_puma <- zip_puma %>% 
  filter(state == "25") %>% 
  select(zcta5, PUMAname, pop10) %>% 
  rename(zip = zcta5,
         puma = PUMAname,
         zip.pop = pop10)

zip_puma$zip <- as.numeric(as.character(zip_puma$zip))
zip_puma$zip.pop <- as.numeric(as.character(zip_puma$zip.pop))
zip_puma$puma <- as.character(zip_puma$puma)
zip_puma$puma <- as.factor(zip_puma$puma)

zip_puma <- zip_puma %>% 
  filter(zip < 99999)

puma_zip <- merge(x = puma, y = zip_puma, by = c("puma"), all.x = TRUE)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
#sample
df <- data %>% 
  select(Vrid, var21) %>% 
  rename(zip = var21,
         ID = Vrid)
  
df$zip <- as.numeric(as.character(df$zip))
df$ID <- as.numeric(as.character(df$ID))

df <- merge(x = df, y = puma_zip, by = c("zip"), all.x = TRUE)

#df <- df %>% 
#  select(ID, zip, puma, zip_pop)

df <- df %>% 
  group_by(ID) %>% 
  mutate(total.puma = sum(puma.pop),
         puma.weight = puma.pop/total.puma)

df <- df %>% 
  select(ID, zip, puma, puma.weight)

puma_zip <- puma_zip %>% 
  select(puma, zip)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
data$zip <- as.numeric(as.character(data$var21))

df$Vrid <- df$ID

#merge demos (don't need to do that)
#data <- merge(x = d, y = data, by = c("ethnicity", "age_group", "sex"), all.y = #TRUE)

data <- data %>% 
  unite(demo, ethnicity, sex, age_group, remove = FALSE)

#dont need to do that
#data <- merge(x = df, y = data, by = "zip", all.y = TRUE)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
demo <- demo %>%
  unite(demo, ethnicity, sex, age_group, remove = FALSE)

d <- d %>%
  unite(demo, ethnicity, sex, age_group, remove = FALSE)

demo <- merge(x = d, y = demo, by = c("demo"), all.x = TRUE)

demo.dist <- data.frame(demo = demo$demo,
                       Freq = nrow(data) * demo$pop.demo.prop.x)

#demo.dist$demo <- as.character(demo.dist$demo)

#puma.dist <- data.frame(puma = puma$puma,
#                        Freq = nrow(data) * puma$puma_prop)

zip1 <- merge(x = df, y = pop_zip, by = "zip", all.x = TRUE)

zip.dist <- data.frame(zip = zip1$zip,
                             Freq = nrow(data) * zip1$pop.zip.prop)

# Create the un-weighted survey object
svy.unweighted <- svydesign(ids = ~ 1, data = data)

#data <- data %>% rename(zip = zip.x)

# Create survey design object with weights
svy.rake <- rake(design = svy.unweighted,
                   sample.margins = list(~demo, ~zip),
                   population.margins = list(demo.dist, zip.dist))

summary(weights(svy.rake))

#svy.rake.trim <- trimWeights(svy.rake, lower = 0.3, upper = 3, strict = TRUE)

# Extract weight values
wt <- data.frame(wt = weights(svy.rake))

# Bind weights with the df, re-order variable
data <- cbind(data, wt)

data <- data %>% 
  select(wt, ID:var15)
```

### Research Overview

- Sampled 1,120 adult residents of the Boston core-based statistical area (CBSA), quota matched on age, gender, and ethnicity and weighted by ZIP.
- For each MIP behavior, measured current self-reported *adoption*, *intention to adopt in the future*, and three social expectation measures - *belief that others are adopting the behavior*, *belief that others should adopt the behavior*, and *belief that others think people should adopt the behavior*.
- For each MIP behavior, measured stated *interest in participating in a program* which helps adopt the behavior. 
- For six out of seven MIP behaviors, measured perceived relative *carbon mitigation impact* of that behavior compared to a list of low-impact behaviors.

### Results

#### Program Participation Interest

##### How interested would you be in participating in a program which helps you *[adopt behavior]*?
```{r, fig.width = 9, fig.height = 5, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
#Boxplot in violin

# Violin plot of interest in program
violin <- data %>% 
  select(wt,
         var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

violin <- mutate_all(violin, function(x) as.numeric(as.character(x)))

violin_plot0 <- violin %>%
   pivot_longer(
   cols = starts_with(c("var")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>% 
    mutate(behavior = recode(behavior, var96 = "Purchase \nan EV", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste"))

p <- ggplot(violin_plot0, aes(x = reorder(behavior, -value), y = value)) + 
  geom_violin()

p + geom_boxplot(width = 0.1, color = "grey") + 
  stat_summary(fun.y = median, geom = "point", size = 2, color = "red") + 
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  labs(x = "",y = "Interest in a program which helps adopt behaviors") + 
scale_y_continuous(breaks= pretty_breaks())
```

```{r, fig.width = 9, fig.height = 5, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, eval = FALSE}
### Interest in program participation Unweighted

# Violin plot of interest in program
violin <- data %>% 
  select(var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

dodge <- position_dodge(width = 1)

violin_plot <- violin %>%
    select(var96:var110) %>%
    gather(behavior, value) %>%
    mutate(behavior = recode(behavior, var96 = "Purchase an \nelectric car", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste")) %>%
  ggplot(aes(x = reorder(as_factor(behavior), -value), y = value, fill = value)) +
    geom_violin() +
  geom_boxplot(position = dodge, width = 0.1, color = "grey", alpha = 0.2, outlier.shape = NA) +
    stat_summary(fun.y = median, geom = "point", size = 2, color = "red") +
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  #scale_y_continuous(labels = function(x) paste0(x,"%")) +
  labs(x ="",y = "Interest in a program which helps adopt behaviors")

violin_plot
#ggsave("violin_plot.png", units = "in", width = 8, height = 5, dpi = 300)
```

```{r, fig.width = 9, fig.height = 5, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, eval = FALSE}
### Interest in program participation Demo Weighted

# Violin plot of interest in program
violin <- data %>% 
  select(demo_weight,
         var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

violin <- mutate_all(violin, function(x) as.numeric(as.character(x)))

dodge <- position_dodge(width = 1)

violin_plot1 <- violin %>%
   pivot_longer(
   cols = starts_with(c("var")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>% 
    mutate(behavior = recode(behavior, var96 = "Purchase an \nelectric car", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste")) %>%
  ggplot(aes(x = reorder(as_factor(behavior), -value), y = value, fill = value, weight = demo_weight)) +
    geom_violin() +
  geom_boxplot(position = dodge, width = 0.1, color = "grey", alpha = 0.2, outlier.shape = NA) +
    stat_summary(fun.y = median, geom = "point", size = 2, color = "red") +
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  #scale_y_continuous(labels = function(x) paste0(x,"%")) +
  labs(x ="",y = "Interest in a program which helps adopt behaviors")

violin_plot1

#ggsave("violin_plot.png", units = "in", width = 8, height = 5, dpi = 300)
```

```{r, fig.width = 9, fig.height = 5, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, eval = FALSE}
### Interest in program participation ZIP Weighted
# Violin plot of interest in program
violin <- data %>% 
  select(zip.weight,
         var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

violin <- mutate_all(violin, function(x) as.numeric(as.character(x)))

dodge <- position_dodge(width = 1)

violin_plot2 <- violin %>%
   pivot_longer(
   cols = starts_with(c("var")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>% 
    mutate(behavior = recode(behavior, var96 = "Purchase an \nelectric car", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste")) %>%
  ggplot(aes(x = reorder(as_factor(behavior), -value), y = value, fill = value, weight = zip.weight)) +
    geom_violin() +
  geom_boxplot(position = dodge, width = 0.1, color = "grey", alpha = 0.2, outlier.shape = NA) +
    stat_summary(fun.y = median, geom = "point", size = 2, color = "red") +
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  #scale_y_continuous(labels = function(x) paste0(x,"%")) +
  labs(x ="",y = "Interest in a program which helps adopt behaviors")

violin_plot2

#ggsave("violin_plot.png", units = "in", width = 8, height = 5, dpi = 300)
```

```{r, echo = FALSE, results = 'asis', message = FALSE}
## Index table
index <- data %>% 
  select(
  wt,
  Vrid,
  var13, #RID
  var83O227:var83O804, #ranking
  -var83O800, -var83O797, #remove buying used clothes & composting
  #EV
  var26, #adoption
  var87, #EE
  var28, #PNB,
  var88, #NE
  var94, #intent
  var96, #program interest
  #Fly
  var70, #Are you trying to fly less frequently than you used to?
  var69, #EE
  var38, #PNB
  var35, #NE
  var97, #intent
  var98, #program interest
  #Offsets
  var39, #adoption
  var40, #EE
  var41, #PNB
  var42, #NE
  var99, #intent
  var100, #program interest
  #PBD
  var71, #Are you trying to eat less meat than you used to?
  #var115, #adoption % of meals
  var72, #EE
  var66, #PNB
  var48, #NE
  var103, #intent
  var104, #program interest
  #RECs
  var54, #adoption
  var55, #EE
  var56, #PNB
  var57, #NE
  var105, #intent
  var106, #program interest
  #Solar
  var59, #adoption
  var60, #EE
  var61, #PNB
  var62, #NE
  var107, #intent
  var108, #program interest
  #Food waste
  var73, #Are you currently trying to reduce the amount of food waste you produce?
  var74, #EE
  var75, #PNB
  var76, #NE
  var109, #intent
  var110 #program interest
  ) %>% 
  rename(
  offset_hrank = var83O227,
  ev_hrank = var83O794,
  recs_hrank = var83O796,
  solar_hrank = var83O793,
  pbd_hrank = var83O795,
  fly_hrank = var83O228,
  local_lrank = var83O798,
  bulbs_lrank = var83O799,
  fridge_lrank = var83O801,
  trees_lrank = var83O802,
  recycling_lrank = var83O803,
  pack_lrank = var83O804,
  #EV
  ev_adoption = var26,
  ev_ee = var87,
  ev_pnb = var28,
  ev_ne = var88,
  ev_intent = var94,
  ev_program_interest = var96,
  #Fly
  fly_adoption = var70, #trying to fly less
  fly_ee = var69, #EE
  fly_pnb = var38, #PNB
  fly_ne = var35, #NE
  fly_intent = var97,
  fly_program_interest = var98,
  #Offset
  offset_adoption = var39, #adoption
  offset_ee = var40, #EE
  offset_pnb = var41, #PNB
  offset_ne = var42, #NE
  offset_program_interest = var100, #program interest
  offset_intent = var99,
  #PBD
  pbd_adoption = var71, #trying to
  pbd_ee = var72, #EE
  pbd_pnb = var66, #PNB
  pbd_ne = var48, #NE
  pbd_program_interest = var104, #program interest
  pbd_intent = var103, 
  #RECs
  recs_adoption = var54, #adoption
  recs_ee = var55, #EE
  recs_pnb = var56, #PNB
  recs_ne = var57, #NE
  recs_program_interest = var106, #program interest
  recs_intent = var105,
  #Solar
  solar_adoption = var59, #adoption
  solar_ee = var60, #EE
  solar_pnb = var61, #PNB
  solar_ne = var62, #NE
  solar_program_interest = var108, #program interest
  solar_intent = var107,
  #Food waste
  foodwaste_adoption = var73, #attempt
  foodwaste_ee = var74, #EE
  foodwaste_pnb = var75, #PNB
  foodwaste_ne = var76, #NE
  foodwaste_program_interest = var110, #program interest
  foodwaste_intent = var109)

index <- index %>% 
  mutate(
  #Adoption
  ev_adoption = case_when(ev_adoption == 0 ~ 0, TRUE ~ 1), 
  fly_adoption = case_when(fly_adoption == 1 ~ 1, TRUE ~ 0),
  recs_adoption = case_when(recs_adoption == 1 ~ 1, TRUE ~ 0),
  pbd_adoption = case_when(pbd_adoption == 1 ~1, TRUE ~ 0),
  #EE
  ev_ee = ev_ee/10,
  fly_ee = fly_ee/10,
  solar_ee = solar_ee/10,
  recs_ee = recs_ee/10,
  offset_ee = offset_ee/10,
  foodwaste_ee = foodwaste_ee/10,
  pbd_ee = pbd_ee/10,
  #PNB - recoded
  fly_pnb = case_when(fly_pnb == 10144 ~ 0, TRUE ~ 1),
  #NE
  ev_ne = ev_ne/10,
  fly_ne = fly_ne/10,
  solar_ne = solar_ne/10,
  recs_ne = recs_ne/10,
  offset_ne = offset_ne/10,
  foodwaste_ne = foodwaste_ne/10,
  pbd_ne = pbd_ne/10,
  #Intent - recoded
  fly_intent = case_when(fly_intent == 0 ~ 0, fly_intent == 10 ~ 1, fly_intent == 20 ~ 2, fly_intent == 30 ~ 3, fly_intent == 40 ~ 4, fly_intent == 50 ~ 5, fly_intent == 60 ~ 6, fly_intent == 70 ~ 7, fly_intent == 80 ~ 8, fly_intent == 10571 ~ 9, TRUE ~ 10),
  #Program interest
  ev_program_interest = ev_program_interest/10,
  fly_program_interest = fly_program_interest/10,
  solar_program_interest = solar_program_interest/10,
  recs_program_interest = recs_program_interest/10,
  offset_program_interest = offset_program_interest/10,
  foodwaste_program_interest = foodwaste_program_interest/10,
  pbd_program_interest = pbd_program_interest/10,
  #Intent
  ev_intent = ev_intent/100,
  fly_intent = fly_intent/10, # needs recoding
  solar_intent = solar_intent/100,
  recs_intent = recs_intent/100,
  offset_intent = offset_intent/100,
  foodwaste_intent = foodwaste_intent/100,
  pbd_intent = pbd_intent/100)

# ranking

df1 <- index %>% 
  select(Vrid:pack_lrank)

df1 = index %>% 
     transmute(Vrid, across(ends_with('hrank'), 
        ~  rowSums(. <  select(df1, ends_with('lrank'))), .names = '{.col}_rank'))

df1 <- mutate_all(df1, function(x) as.numeric(as.character(x)))

#

index_long <- index %>% 
  select(Vrid, wt, ev_adoption:foodwaste_program_interest)

index_long <- mutate_all(index_long, function(x) as.numeric(as.character(x)))

index_long <- left_join(index_long, df1, by = "Vrid")

index_long <- index_long %>%
 pivot_longer(
   cols = ends_with(c("intent", "program_interest", "ee", "pnb", "ne", "adoption", "rank")),
   names_to = "indicator",
   values_to = "value",
   values_drop_na = TRUE)

index_long <- index_long %>%
  mutate(behavior = indicator)

fin_table <- index_long %>% 
  mutate(behavior = sapply(strsplit(index_long$indicator, split='_', fixed=TRUE),function(x) (x[1])))

fin_table <- fin_table %>% 
  mutate(ind = sapply(strsplit(fin_table$indicator, split='_', fixed=TRUE),function(x) (x[2])))

t <- group_by(fin_table, behavior, ind)

t <- summarise(t, value.mean = mean(value, na.rm = TRUE))

t <- t %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = value.mean)

t <- t %>% 
  mutate(hrank = hrank/6)
```

```{r, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
# Function by Greg Lin
# Notice bias here = a positive number. 
# Higher values give more widely spaced colors at the high end

make_color_pal <- function(colors, bias = 1) {
  get_color <- colorRamp(colors, bias = bias)
  function(x) rgb(get_color(x), maxColorValue = 255)
}

good_color <- make_color_pal(c("#ffffff", "#f2fbd2", "#c9ecb4", "#93d3ab", "#35b0ab"), bias = 2)

# Generate a vector of example numbers between 0 and 1
seq(0.1, 0.9, length.out = 12)
# [1] 0.1000000 0.1727273 0.2454545 0.3181818 0.3909091 0.4636364
# [7] 0.5363636 0.6090909 0.6818182 0.7545455 0.8272727 0.9000000
# create matching colors
good_color(seq(0.1, 0.9, length.out = 12))
# [1] "#E9F8CB" "#D9F2C0" "#C9ECB4" "#BDE6B2" "#B0E0AF" "#A4DAAD"
# [7] "#97D5AB" "#88CFAB" "#79C9AB" "#69C3AB" "#5ABDAB" "#4AB8AB"
# display the colors
seq(0.1, 0.9, length.out = 12) %>% 
  good_color() %>% 
  scales::show_col()
```

#### Boston Index

```{r, echo = FALSE, results = 'asis', message = FALSE}
### Boston Index (weighted by ZIP and age-sex-ethnicity)
t11 <- group_by(fin_table, behavior, ind)

t11 <- summarise(t11, w.mean = weighted.mean(value, wt, na.rm = TRUE))

t11 <- t11 %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = w.mean)

t11 <- t11 %>% 
  mutate(hrank = hrank/6)

# Rename columns
t11 <- t11 %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t11$Behavior[t11$Behavior == "ev"] <- "Purchase an EV"
t11$Behavior[t11$Behavior == "fly"] <- "Fly less*"
t11$Behavior[t11$Behavior == "offset"] <- "Purchase carbon offsets"
t11$Behavior[t11$Behavior == "recs"] <- "Purchase green energy"
t11$Behavior[t11$Behavior == "solar"] <- "Install solar panels"
t11$Behavior[t11$Behavior == "pbd"] <- "Eat less meat*"
t11$Behavior[t11$Behavior == "foodwaste"] <- "Waste less food*"

t11 <- t11 %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

orange_pal <- function(x) rgb(colorRamp(c("#ffe4cc", "#ff9500"))(x), maxColorValue = 255)

tt = reactable(t11,
  style = list(fontSize = "12px"),
  defaultSortOrder = 'asc',
  defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = TRUE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center",
      minWidth = 100),
  # Add theme for the top border
    theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )
    ),
  columns = list(
    Behavior = colDef(
      minWidth = 170,
      align = "left"),
    Adoption = colDef(
      style = function(value) {
    normalized <- (value - min(t11$Adoption)) / (max(t11$Adoption) - min(t11$Adoption))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    Intention = colDef(
      style = function(value) {
    normalized <- (value - min(t11$Intention)) / (max(t11$Intention) - min(t11$Intention))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `Belief that others are engaging in the behavior` = colDef(
      style = function(value) {
    normalized <- (value - min(t11$`Belief that others are engaging in the behavior`)) / (max(t11$`Belief that others are engaging in the behavior`) - min(t11$`Belief that others are engaging in the behavior`))
    color <- good_color(normalized)
    list(background = color)
  },
      name = "Others have adopted",
      format = colFormat(digits = 2)),
    `Belief that others should engage in the behavior` = colDef(
       style = function(value) {
    normalized <- (value - min(t11$`Belief that others should engage in the behavior`)) / (max(t11$`Belief that others should engage in the behavior`) - min(t11$`Belief that others should engage in the behavior`))
    color <- good_color(normalized)
    list(background = color)
  },
      name = "Others should adopt",
      format = colFormat(digits = 2)),
    `Belief that others think people should engage in the behavior` = colDef(
      style = function(value) {
    normalized <- (value - min(t11$`Belief that others think people should engage in the behavior`)) / (max(t11$`Belief that others think people should engage in the behavior`) - min(t11$`Belief that others think people should engage in the behavior`))
    color <- good_color(normalized)
    list(background = color)
  },
      name = "Others think people should adopt",
      format = colFormat(digits = 2),
      minWidth = 120),
    `Program interest` = colDef(
      style = function(value) {
    normalized <- (value - min(t11$`Program interest`)) / (max(t11$`Program interest`) - min(t11$`Program interest`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 70),
    `Carbon impact ranking` = colDef(
      format = colFormat(digits = 2))),
  
  columnGroups = list(
    colGroup(name = "Beliefs that...", columns = c("Belief that others are engaging in the behavior", "Belief that others should engage in the behavior", "Belief that others think people should engage in the behavior"))))

div(
  class = "Behavior",
  div(
    # this can be called with CSS now via .title
    #class = "title",
    #h2("MIP Index: Boston"),
    "The survey was fielded from March 31 – April 21, 2021, drawing on the stratified sample of the Boston CBSA (n = 1,120)
    "
  ),
  # The actual table
  tt)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
### Boston Index Unweighted
# Rename columns
t <- t %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t$Behavior[t$Behavior == "ev"] <- "Purchase an EV"
t$Behavior[t$Behavior == "fly"] <- "Fly less*"
t$Behavior[t$Behavior == "offset"] <- "Purchase carbon offsets"
t$Behavior[t$Behavior == "recs"] <- "Purchase green energy"
t$Behavior[t$Behavior == "solar"] <- "Install solar panels"
t$Behavior[t$Behavior == "pbd"] <- "Eat less meat*"
t$Behavior[t$Behavior == "foodwaste"] <- "Waste less food*"

t <- t %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

reactable(t,
  columns = list(Adoption = colDef(format = colFormat(digits = 2), minWidth = 90),
                 Intention = colDef(format = colFormat(digits = 2), minWidth = 90),
                 `Belief that others are engaging in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others think people should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Program interest` = colDef(format = colFormat(digits = 2)),
                 `Carbon impact ranking` = colDef(format = colFormat(digits = 2))),
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))
```


```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
### Boston Index Demo Weighted
t1 <- group_by(fin_table, behavior, ind)

t1 <- summarise(t1, w.mean = weighted.mean(value, demo_weight, na.rm = TRUE))

t1 <- t1 %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = w.mean)

t1 <- t1 %>% 
  mutate(hrank = hrank/6)
# Rename columns
t1 <- t1 %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t1$Behavior[t1$Behavior == "ev"] <- "Purchase an EV"
t1$Behavior[t1$Behavior == "fly"] <- "Fly less*"
t1$Behavior[t1$Behavior == "offset"] <- "Purchase carbon offsets"
t1$Behavior[t1$Behavior == "recs"] <- "Purchase green energy"
t1$Behavior[t1$Behavior == "solar"] <- "Install solar panels"
t1$Behavior[t1$Behavior == "pbd"] <- "Eat less meat*"
t1$Behavior[t1$Behavior == "foodwaste"] <- "Waste less food*"

t1 <- t1 %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

reactable(t1,
  columns = list(Adoption = colDef(format = colFormat(digits = 2), minWidth = 90),
                 Intention = colDef(format = colFormat(digits = 2), minWidth = 90),
                 `Belief that others are engaging in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others think people should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Program interest` = colDef(format = colFormat(digits = 2)),
                 `Carbon impact ranking` = colDef(format = colFormat(digits = 2))),
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
### Boston Index ZIP weighted
t2 <- group_by(fin_table, behavior, ind)

t2 <- summarise(t2, w.mean = weighted.mean(value, zip.weight, na.rm = TRUE))

t2 <- t2 %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = w.mean)

t2 <- t2 %>% 
  mutate(hrank = hrank/6)

# Rename columns
t2 <- t2 %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t2$Behavior[t2$Behavior == "ev"] <- "Purchase an EV"
t2$Behavior[t2$Behavior == "fly"] <- "Fly less*"
t2$Behavior[t2$Behavior == "offset"] <- "Purchase carbon offsets"
t2$Behavior[t2$Behavior == "recs"] <- "Purchase green energy"
t2$Behavior[t2$Behavior == "solar"] <- "Install solar panels"
t2$Behavior[t2$Behavior == "pbd"] <- "Eat less meat*"
t2$Behavior[t2$Behavior == "foodwaste"] <- "Waste less food*"

t2 <- t2 %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

reactable(t2,
  columns = list(Adoption = colDef(format = colFormat(digits = 2), minWidth = 90),
                 Intention = colDef(format = colFormat(digits = 2), minWidth = 90),
                 `Belief that others are engaging in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others think people should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Program interest` = colDef(format = colFormat(digits = 2)),
                 `Carbon impact ranking` = colDef(format = colFormat(digits = 2))),
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))
```

For eating less meat, flying less, and reducing food waste, adoption variable measured current attempt, rather than reported adoption (e.g., *Are you trying to fly less frequently than you used to?*)

#### Carbon Impact Ranking

The table below presents average ranking in terms of carbon mitigation potential of MIP (highlighted) and low-impact behaviors assigned by participants. For example, on average, installing rooftop solar was assigned rank 4.62 out of 12.

```{r, echo = FALSE, results = 'asis', message = FALSE, fig.align = 'center'}
#Ranking table
ranking_table <- index %>% 
  select(Vrid, offset_hrank:pack_lrank) %>% 
  pivot_longer(
   cols = ends_with(c("rank")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>%
  group_by(behavior) %>% 
  summarise(mean = mean(value))

# Rename columns
ranking_table <- ranking_table %>% 
  rename('Behavior' = behavior,
         'Average ranking' = mean)

# Rename rows
ranking_table$Behavior[ranking_table$Behavior == "solar_hrank"] <- "Get 100% of electricity from solar panels on the roof instead of from the grid for one year"
ranking_table$Behavior[ranking_table$Behavior == "recycling_lrank"] <- "Recycle 100% of recyclable materials generated as waste, including newspaper, magazines, glass, plastic, and metal for one year"
ranking_table$Behavior[ranking_table$Behavior == "recs_hrank"] <- "Purchase 100% of household energy from renewable sources for one year"
ranking_table$Behavior[ranking_table$Behavior == "ev_hrank"] <- "Drive a fully electric car for one year"
ranking_table$Behavior[ranking_table$Behavior == "trees_lrank"] <- "Plant 10 trees"
ranking_table$Behavior[ranking_table$Behavior == "bulbs_lrank"] <- "Replace 25 incandescent light bulbs with ENERGY STAR lights"
ranking_table$Behavior[ranking_table$Behavior == "fridge_lrank"] <- "Replace old refrigerator with ENERGY STAR refrigerator"
ranking_table$Behavior[ranking_table$Behavior == "offset_hrank"] <- "Purchase carbon offsets to offset average American’s annual carbon footprint"
ranking_table$Behavior[ranking_table$Behavior == "pack_lrank"] <- "Eliminate all food packaging for one year"
ranking_table$Behavior[ranking_table$Behavior == "local_lrank"] <- "Source all of food locally for one year"
ranking_table$Behavior[ranking_table$Behavior == "fly_hrank"] <- "Take one fewer round-trip flight"
ranking_table$Behavior[ranking_table$Behavior == "pbd_hrank"] <- "Avoid eating all meat for one year"

ranking_t = reactable(ranking_table,
  style = list(fontSize = "12px"),
  defaultPageSize = 12,
  defaultSortOrder = 'asc',
  defaultSorted = 'Average ranking',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = FALSE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center",
      minWidth = 100),
  # Add theme for the top border
    theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )
    ),
  columns = list(
    Behavior = colDef(
      minWidth = 490,
      align = "left"),
    `Average ranking` = colDef(
      format = colFormat(digits = 2),
      maxWidth = 100)),
  rowStyle = function(index) {
  if (index == 2 | index == 3 | index == 6 | index == 8 |index == 9| index == 11) list(background = "#E9F8CB")
})

ranking_t  
```
