---
title: "Make It Personal: Boston Index Results"
output: html_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
author:
- Erik Thulin, ethulin@rare.org
- Rakhim Rakhimov, rrakhimov@rare.org
---

```{r setup, include = FALSE, echo = FALSE, results = 'asis'}
library(tidyverse)
library(haven)
library(labelled)
library(data.table)
library(knitr)
library(reactable)
library(htmltools)
library(lubridate)
library(hrbrthemes)
library(survey)
options(scipen = 999)
library(scales)
library(fastDummies)
require(lattice)
library(corrr)
library(dotwhisker)

data <- read_sav("spss_4_29_2021.sav")
lucid_data <-read.csv("lucid_response_4_29_2021.csv")
```

```{r, include = FALSE, echo = FALSE, results = 'asis', eval = FALSE}
# Incompletes match between Lucid and Alchemer
lucid <- read.csv("lucid_data_analysis_4_29_2021.csv")

test <- lucid %>% 
  filter(FulcrumStatus == 3 & ClientStatus == 10 & SupplierName != "Z - Test Supplier") %>% 
  mutate(
    var13 = as.character(Response.ID),
    var13 = tolower(var13))

test_merge <- merge(x = data, y = test, by = "var13", all.x = TRUE)

test_merge <- test_merge %>% 
  select(var13, Response.ID)

test_merge$Response.ID <- as.character(test_merge$Response.ID)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
lucid_data <- lucid_data %>% 
  filter(SupplierName != "Z - Test Supplier") %>% # remove test responses
  select(-HISPANIC.3., -REGION.6., -Ethnicity...Detailed.7.) %>% 
  mutate(
    ID = as.character(Response.ID),
    ID = tolower(ID))

data$ID <- data$var13

data <- merge(x = lucid_data, y = data, by = "ID", all.y = TRUE)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
data <- data %>%
select(-PID, -MID, -RespondentSID, -Response.ID, -IsLive, -Survey.Number, -SurveyName, -STATE.4., -ZIP.2., -Vcid, -Vcomment, -Vlanguage, -Vreferer, -Vsessionid, -Vuseragent, -VGeoCountry, -Vpostal, var10, -var112, -var113, -var10) %>% 
rename(sex = var3,
       age = var2,
       White = var8O33,
       Black = var8O34,
       Native_American = var8O35,
       Asian = var8O36,
       Native_Hawaiian = var8O37,
       Other = var8O38,
       ethnicity = ETHNICITY.8.) %>% 
mutate(sex = case_when(sex == 10003 ~ "Male", TRUE ~ "Female"),
       ethnicity = case_when(Vrid == 394 ~ "White", 
                             Vrid == 1008 ~ "Asian", 
                             Vrid == 184 ~ "White", 
                             Vrid == 1505 ~ "Black", 
                             Vrid == 193 ~ "Black",
                             Vrid == 1815 ~ "Black",
                             TRUE ~ ethnicity),
       ethnicity = case_when(ethnicity == 1 ~ "White", 
                             ethnicity == 2 ~ "Black", 
                             ethnicity == 3 ~ "Alaska_Native", 
                             ethnicity == 4 ~ "Asian", 
                             ethnicity == 5 ~ "Asian", 
                             ethnicity == 6 ~ "Asian", 
                             ethnicity == 7 ~ "Asian", 
                             ethnicity == 8 ~ "Asian", 
                             ethnicity == 9 ~ "Asian", 
                             ethnicity == 10 ~ "Asian", 
                             ethnicity == 15 ~ "Other", 
                             TRUE ~ ethnicity)) %>%
  filter(age >= 18 & age <= 150)
```

```{r, include=FALSE, echo = FALSE, warning = FALSE}
#Demo prop
demo <- read.csv("demo_w.csv")

demo <- demo %>% 
  select(-`ï..demo_combined`) %>% 
  filter(prop > 0) %>% 
  rename(sex = gender,
         pop.demo.prop = prop,
         ethnicity = race)

# Create age brackets
agebreaks <- c(18, 25, 35, 45, 55, 65, 100)
agelabels <- c("18-24", "25-34", "35-44", "45-54", "55-64", "65+")
# Add age brackets to df
setDT(data)[ , age_group := cut(age, 
                                breaks = agebreaks, 
                                right = FALSE, 
                                labels = agelabels)]

data$ethnicity <- as.factor(data$ethnicity)

#Demo sample
#Counting demos in sample
d <- data %>% 
  select(Vrid, sex, age_group, ethnicity)

d <- d %>% 
  group_by(sex, ethnicity, age_group) %>%
  summarise(count=n()) 

d <- d %>% 
  mutate(sample.demo.prop = count/sum(d$count))

#Merging population and sample demos. Demo groups in pop need to be the same as demo groups in sample.

d <- merge(x = d, y = demo, by = c("ethnicity", "age_group", "sex"), all.x = TRUE)

#d <- d %>% 
#  mutate(demo_weight = pop.demo.prop/sample.demo.prop) 

#d <- d %>% select(ethnicity, age_group, sex, demo_weight)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
# ZIP weight population
pop_zip <- read.csv("geocorr_cbsa_zip.csv")

pop_zip <- pop_zip %>% 
  filter(cbsa == "14460") %>% 
  select(-cbsa, -cbsaname15, -zipname)

pop_zip$zip <- as.numeric(as.character(pop_zip$zcta))
pop_zip$zip.pop <- as.numeric(as.character(pop_zip$pop10))
pop_zip$pop.zip.prop <- as.numeric(as.character(pop_zip$afact))

pop_zip <- pop_zip %>% 
  filter(zip < 99999) %>% 
  select(zip, zip.pop, pop.zip.prop)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
#ZIP weight sample
df <- data %>% 
  select(Vrid, var21)
  
df$zip <- as.numeric(as.character(df$var21))
df$ID <- as.numeric(as.character(df$Vrid))

df <- df %>% 
  select(ID, zip)%>% 
  gather(ID, zip) %>% 
  group_by(zip) %>%
  summarise(count=n()) 

df <- df %>% 
  mutate(sample.zip.prop = count/sum(count))

df <- merge(df, pop_zip, by = "zip")

df <- df %>% 
  mutate(zip.weight = pop.zip.prop/sample.zip.prop)

df <- df %>% 
  select(zip, zip.weight)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
### weighting by puma
#population
puma <- read.csv("geocorr_puma_export.csv")

puma <- puma %>% 
  filter(cbsa == "14460") %>% 
  select(PUMAname, pop10) %>% 
  rename(puma = PUMAname,
         puma.pop = pop10)

puma$puma.pop <- as.numeric(as.character(puma$puma.pop))

puma$puma <- as.character(puma$puma)
puma$puma <- as.factor(puma$puma)

puma <- puma %>% 
  mutate(pop.puma.prop = puma.pop/sum(puma.pop))
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
#DF matching ZIPs to PUMAs
zip_puma <- read.csv("geocorr_puma_zip.csv")

zip_puma <- zip_puma %>% 
  filter(state == "25") %>% 
  select(zcta5, PUMAname, pop10) %>% 
  rename(zip = zcta5,
         puma = PUMAname,
         zip.pop = pop10)

zip_puma$zip <- as.numeric(as.character(zip_puma$zip))
zip_puma$zip.pop <- as.numeric(as.character(zip_puma$zip.pop))
zip_puma$puma <- as.character(zip_puma$puma)
zip_puma$puma <- as.factor(zip_puma$puma)

zip_puma <- zip_puma %>% 
  filter(zip < 99999)

puma_zip <- merge(x = puma, y = zip_puma, by = c("puma"), all.x = TRUE)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
#sample PUMAs
df <- data %>% 
  select(Vrid, var21) %>% 
  rename(zip = var21,
         ID = Vrid)
  
df$zip <- as.numeric(as.character(df$zip))
df$ID <- as.numeric(as.character(df$ID))

df <- merge(x = df, y = puma_zip, by = c("zip"), all.x = TRUE)

#df <- df %>% 
#  select(ID, zip, puma, zip_pop)

df <- df %>% 
  group_by(ID) %>% 
  mutate(total.puma = sum(puma.pop),
         puma.weight = puma.pop/total.puma)

df <- df %>% 
  select(ID, zip, puma, puma.weight)

puma_zip <- puma_zip %>% 
  select(puma, zip)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
data$zip <- as.numeric(as.character(data$var21))

df$Vrid <- df$ID

#merge demos (don't need to do that)
#data <- merge(x = d, y = data, by = c("ethnicity", "age_group", "sex"), all.y = #TRUE)

data <- data %>% 
  unite(demo, ethnicity, sex, age_group, remove = FALSE)

#dont need to do that
#data <- merge(x = df, y = data, by = "zip", all.y = TRUE)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
demo <- demo %>%
  unite(demo, ethnicity, sex, age_group, remove = FALSE)

d <- d %>%
  unite(demo, ethnicity, sex, age_group, remove = FALSE)

demo <- merge(x = d, y = demo, by = c("demo"), all.x = TRUE)

demo.dist <- data.frame(demo = demo$demo,
                       Freq = nrow(data) * demo$pop.demo.prop.x)

#demo.dist$demo <- as.character(demo.dist$demo)

#puma.dist <- data.frame(puma = puma$puma,
#                        Freq = nrow(data) * puma$puma_prop)

zip1 <- merge(x = df, y = pop_zip, by = "zip", all.x = TRUE)

zip.dist <- data.frame(zip = zip1$zip,
                             Freq = nrow(data) * zip1$pop.zip.prop)

# Create the un-weighted survey object
svy.unweighted <- svydesign(ids = ~ 1, data = data)

#data <- data %>% rename(zip = zip.x)

# Create survey design object with weights
svy.rake <- rake(design = svy.unweighted,
                   sample.margins = list(~demo, ~zip),
                   population.margins = list(demo.dist, zip.dist))

svy.rake.demo <- rake(design = svy.unweighted,
                   sample.margins = list(~demo),
                   population.margins = list(demo.dist))

summary(weights(svy.rake))
summary(weights(svy.rake.demo))

#svy.rake.trim <- trimWeights(svy.rake, lower = 0.3, upper = 3, strict = TRUE)

# Extract weight values
wt <- data.frame(wt = weights(svy.rake))

# Bind weights with the df, re-order variable
data <- cbind(data, wt)

data <- data %>% 
  select(wt, ID:age_group)
```

### Research Overview

- Sampled 1,155 adult residents of the Boston core-based statistical area (CBSA), quota matched on age, gender, and ethnicity and weighted by ZIP
- For each MIP behavior:
  + Measured current self-reported *adoption*, *intention to adopt in the future*, and three social expectation measures - *belief that others are adopting the behavior*, *belief that others should adopt the behavior*, and *belief that others think people should adopt the behavior*
  + Measured stated *interest in participating in a program* that helps adopt the behavior
- For six out of seven MIP behaviors, measured perceived relative *carbon mitigation impact* of that behavior compared to a list of low-impact behaviors

### Results Overview

#### General trends  
* Higher reported adoption of MIP behaviors among Boston residents compared to the general population
  + Reported flying frequency and food waste reduction measures are not reported due to the difference in survey items between the two samples
```{r, echo = FALSE, results = 'asis', message = FALSE}
Behavior <- c("% of households that own at least 1 EV", "% of people that bought a carbon offset in the last year", "% of households that get electricity from a green energy provider", "% of households that have solar panels", "% of people's meals that do not include meat")
`Boston sample` <- c("15%", "6%", "15%", "11%", "5%")
`General population` <- c("11%", "2%", "9%", "4%", "6%")

df <- data.frame(Behavior, `Boston sample`, `General population`)

df = reactable(df,
  style = list(fontSize = "12px"),
  defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = FALSE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center",
      minWidth = 100),
  # Add theme for the top border
    theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )
    ),
  columns = list(
    Behavior = colDef(
      minWidth = 360,
      align = "left"),
    `General.population` = colDef(
      name = "General population",
      minWidth = 140,
      align = "left"),
    `Boston.sample` = colDef(
      name = "Boston sample",
      minWidth = 100,
      align = "left")))

df
```
- Lack of awareness about the relative climate impact of low-impact and high-impact behaviors
  + People underestimate the impact of several MIP actions, including flying less and eating less meat
  + Lack of knowledge about how carbon offsets work
  + People overestimate the impact of low-impact behaviors, including recycling, replacing bulbs, and planting trees
- People underestimate how many people think they should adopt the behaviors
  + There is a large difference between the *perceived % of the population thinking people should adopt these behaviors* and the *actual % of the population thinking people should adopt the behaviors*

#### Program interest  
* Interest in one program is predictive of interest in another program
  + People that are interested in one program are also likely to be interested in another program
* Program interest is the highest for buying an EV, reducing food waste, and contracting for green energy
* Program interest is the lowest for installing solar, buying offsets, eating less meat, and flying less frequently
* Beliefs about what should be done and beliefs about what other's think should be done predict the interest
* Income does not predict program interest
* Ethnicity is a weak predictor of interest
* Education is predictive of program interest
  + This is especially true for those with graduate degrees
  + Education confounds the relationship between income and program interest (Once we add education into the linear regression, coefficients for income are reduced)
* Participation in and donation to religious groups is not correlated with program interest
* Participation in and donation to other social organizations is weakly correlated with program interest
* Being retired is negatively correlated with interest in programs and intention to adopt the behaviors

#### Intention to adopt
* Intention to adopt the behaviors is the highest for reducing food waste and flying less
* Intention to adopt is moderate for purchasing an EV, eating less meat, and contracting for green energy
* Intention to adopt is the lowest for offsets and solar panels
* Moderate correlations between various behaviors, suggesting that some behaviors could be offered in a bundle:
  + Buy an EV and buy offsets
  + Buy offsets and install solar
  + Eat less meat and reduce food waste
  + Contract for green energy and install solar
* All three social expectations are moderate predictors of intention to adopt the behaviors

### Results in Detail

#### Program Participation Interest

##### How interested would you be in participating in a program which helps you *[adopt behavior]*?
```{r, fig.width = 9, fig.height = 5, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
#Boxplot in violin

# Violin plot of interest in program
violin <- data %>% 
  select(wt,
         var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

violin <- mutate_all(violin, function(x) as.numeric(as.character(x)))

violin_plot0 <- violin %>%
   pivot_longer(
   cols = starts_with(c("var")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>% 
    mutate(behavior = recode(behavior, var96 = "Purchase \nan EV", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste"))

p <- ggplot(violin_plot0, aes(x = reorder(behavior, -value), y = value)) + 
  geom_violin()

p + geom_boxplot(width = 0.1, color = "grey") + 
  stat_summary(fun.y = median, geom = "point", size = 2, color = "red") + 
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  labs(x = "",y = "Interest in a program which helps adopt behaviors") + 
scale_y_continuous(breaks= pretty_breaks())
```

```{r, fig.width = 9, fig.height = 5, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, eval = FALSE}
### Interest in program participation Unweighted

# Violin plot of interest in program
violin <- data %>% 
  select(var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

dodge <- position_dodge(width = 1)

violin_plot <- violin %>%
    select(var96:var110) %>%
    gather(behavior, value) %>%
    mutate(behavior = recode(behavior, var96 = "Purchase an \nelectric car", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste")) %>%
  ggplot(aes(x = reorder(as_factor(behavior), -value), y = value, fill = value)) +
    geom_violin() +
  geom_boxplot(position = dodge, width = 0.1, color = "grey", alpha = 0.2, outlier.shape = NA) +
    stat_summary(fun.y = median, geom = "point", size = 2, color = "red") +
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  #scale_y_continuous(labels = function(x) paste0(x,"%")) +
  labs(x ="",y = "Interest in a program which helps adopt behaviors")

violin_plot
#ggsave("violin_plot.png", units = "in", width = 8, height = 5, dpi = 300)
```

```{r, fig.width = 9, fig.height = 5, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, eval = FALSE}
### Interest in program participation Demo Weighted

# Violin plot of interest in program
violin <- data %>% 
  select(demo_weight,
         var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

violin <- mutate_all(violin, function(x) as.numeric(as.character(x)))

dodge <- position_dodge(width = 1)

violin_plot1 <- violin %>%
   pivot_longer(
   cols = starts_with(c("var")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>% 
    mutate(behavior = recode(behavior, var96 = "Purchase an \nelectric car", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste")) %>%
  ggplot(aes(x = reorder(as_factor(behavior), -value), y = value, fill = value, weight = demo_weight)) +
    geom_violin() +
  geom_boxplot(position = dodge, width = 0.1, color = "grey", alpha = 0.2, outlier.shape = NA) +
    stat_summary(fun.y = median, geom = "point", size = 2, color = "red") +
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  #scale_y_continuous(labels = function(x) paste0(x,"%")) +
  labs(x ="",y = "Interest in a program which helps adopt behaviors")

violin_plot1

#ggsave("violin_plot.png", units = "in", width = 8, height = 5, dpi = 300)
```

```{r, fig.width = 9, fig.height = 5, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, eval = FALSE}
### Interest in program participation ZIP Weighted
# Violin plot of interest in program
violin <- data %>% 
  select(zip.weight,
         var96, #EV 
         var98, #Fly
         var100, #Offsets 
         var104, #PBD
         var106, #RECs
         var108, #Solar
         var110) #Foodwaste 

violin <- mutate_all(violin, function(x) as.numeric(as.character(x)))

dodge <- position_dodge(width = 1)

violin_plot2 <- violin %>%
   pivot_longer(
   cols = starts_with(c("var")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>% 
    mutate(behavior = recode(behavior, var96 = "Purchase an \nelectric car", var100 = "Purchase \ncarbon offsets", var106 = "Purchase green \nenergy", var108 = "Install solar \npanels", var98 = "Fly less", var104 = "Eat less meat", var110 = "Reduce food \nwaste")) %>%
  ggplot(aes(x = reorder(as_factor(behavior), -value), y = value, fill = value, weight = zip.weight)) +
    geom_violin() +
  geom_boxplot(position = dodge, width = 0.1, color = "grey", alpha = 0.2, outlier.shape = NA) +
    stat_summary(fun.y = median, geom = "point", size = 2, color = "red") +
  theme(axis.line = element_line(color = "grey"),
        axis.ticks = element_line(color = "grey"),
        axis.title.y = element_text(color = "black", size = 11),
        axis.title.x = element_text(color = "black", size = 11),
        axis.text.x = element_text(colour="black", size = 11),
        axis.text.y = element_text(colour="black", size = 11),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey"),
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill = NA, size = 0.5)) +
  #scale_y_continuous(labels = function(x) paste0(x,"%")) +
  labs(x ="",y = "Interest in a program which helps adopt behaviors")

violin_plot2

#ggsave("violin_plot.png", units = "in", width = 8, height = 5, dpi = 300)
```

```{r, echo = FALSE, results = 'asis', message = FALSE}
## Index table
index <- data %>% 
  select(
  wt,
  Vrid,
  var13, #RID
  var83O227:var83O804, #ranking
  -var83O800, -var83O797, #remove buying used clothes & composting
  #EV
  var26, #adoption
  var87, #EE
  var28, #PNB,
  var88, #NE
  var94, #intent
  var96, #program interest
  #Fly
  var70, #Are you trying to fly less frequently than you used to?
  var69, #EE
  var38, #PNB
  var35, #NE
  var97, #intent
  var98, #program interest
  #Offsets
  var39, #adoption
  var40, #EE
  var41, #PNB
  var42, #NE
  var99, #intent
  var100, #program interest
  #PBD
  var71, #Are you trying to eat less meat than you used to?
  var115, #adoption % of meals
  var72, #EE
  var66, #PNB
  var48, #NE
  var103, #intent
  var104, #program interest
  #RECs
  var54, #adoption
  var55, #EE
  var56, #PNB
  var57, #NE
  var105, #intent
  var106, #program interest
  #Solar
  var59, #adoption
  var60, #EE
  var61, #PNB
  var62, #NE
  var107, #intent
  var108, #program interest
  #Food waste
  var73, #Are you currently trying to reduce the amount of food waste you produce?
  var74, #EE
  var75, #PNB
  var76, #NE
  var109, #intent
  var110 #program interest
  ) %>% 
  rename(
  offset_hrank = var83O227,
  ev_hrank = var83O794,
  recs_hrank = var83O796,
  solar_hrank = var83O793,
  pbd_hrank = var83O795,
  fly_hrank = var83O228,
  local_lrank = var83O798,
  bulbs_lrank = var83O799,
  fridge_lrank = var83O801,
  trees_lrank = var83O802,
  recycling_lrank = var83O803,
  pack_lrank = var83O804,
  #EV
  ev_adoption = var26,
  ev_ee = var87,
  ev_pnb = var28,
  ev_ne = var88,
  ev_intent = var94,
  ev_program_interest = var96,
  #Fly
  fly_adoption = var70, #trying to fly less
  fly_ee = var69, #EE
  fly_pnb = var38, #PNB
  fly_ne = var35, #NE
  fly_intent = var97,
  fly_program_interest = var98,
  #Offset
  offset_adoption = var39, #adoption
  offset_ee = var40, #EE
  offset_pnb = var41, #PNB
  offset_ne = var42, #NE
  offset_program_interest = var100, #program interest
  offset_intent = var99,
  #PBD
  pbd_adoption = var71, #trying to
  pbd_ee = var72, #EE
  pbd_pnb = var66, #PNB
  pbd_ne = var48, #NE
  pbd_program_interest = var104, #program interest
  pbd_intent = var103, 
  #RECs
  recs_adoption = var54, #adoption
  recs_ee = var55, #EE
  recs_pnb = var56, #PNB
  recs_ne = var57, #NE
  recs_program_interest = var106, #program interest
  recs_intent = var105,
  #Solar
  solar_adoption = var59, #adoption
  solar_ee = var60, #EE
  solar_pnb = var61, #PNB
  solar_ne = var62, #NE
  solar_program_interest = var108, #program interest
  solar_intent = var107,
  #Food waste
  foodwaste_adoption = var73, #attempt
  foodwaste_ee = var74, #EE
  foodwaste_pnb = var75, #PNB
  foodwaste_ne = var76, #NE
  foodwaste_program_interest = var110, #program interest
  foodwaste_intent = var109)

index <- index %>% 
  mutate(
  #Adoption
  ev_adoption = case_when(ev_adoption == 0 ~ 0, TRUE ~ 1), 
  recs_adoption = case_when(recs_adoption == 1 ~ 1, TRUE ~ 0),
  #EE
  ev_ee = ev_ee/10,
  fly_ee = fly_ee/10,
  solar_ee = solar_ee/10,
  recs_ee = recs_ee/10,
  offset_ee = offset_ee/10,
  foodwaste_ee = foodwaste_ee/10,
  pbd_ee = pbd_ee/10,
  #NE
  ev_ne = ev_ne/10,
  fly_ne = fly_ne/10,
  solar_ne = solar_ne/10,
  recs_ne = recs_ne/10,
  offset_ne = offset_ne/10,
  foodwaste_ne = foodwaste_ne/10,
  pbd_ne = pbd_ne/10,
  #Program interest
  ev_program_interest = ev_program_interest/10,
  fly_program_interest = fly_program_interest/10,
  solar_program_interest = solar_program_interest/10,
  recs_program_interest = recs_program_interest/10,
  offset_program_interest = offset_program_interest/10,
  foodwaste_program_interest = foodwaste_program_interest/10,
  pbd_program_interest = pbd_program_interest/10,
  #Intent
  ev_intent = ev_intent/100,
  fly_intent = fly_intent/100,
  solar_intent = solar_intent/100,
  recs_intent = recs_intent/100,
  offset_intent = offset_intent/100,
  foodwaste_intent = foodwaste_intent/100,
  pbd_intent = pbd_intent/100)

# ranking

df1 <- index %>% 
  select(Vrid:pack_lrank)

df1 = index %>% 
     transmute(Vrid, across(ends_with('hrank'), 
        ~  rowSums(. <  select(df1, ends_with('lrank'))), .names = '{.col}_rank'))

df1 <- mutate_all(df1, function(x) as.numeric(as.character(x)))

#

index_long <- index %>% 
  select(Vrid, wt, ev_adoption:foodwaste_program_interest)

index_long <- mutate_all(index_long, function(x) as.numeric(as.character(x)))

index_long <- left_join(index_long, df1, by = "Vrid")

index_long <- index_long %>%
 pivot_longer(
   cols = ends_with(c("intent", "program_interest", "ee", "pnb", "ne", "adoption", "rank")),
   names_to = "indicator",
   values_to = "value",
   values_drop_na = TRUE)

index_long <- index_long %>%
  mutate(behavior = indicator)

fin_table <- index_long %>% 
  mutate(behavior = sapply(strsplit(index_long$indicator, split='_', fixed=TRUE),function(x) (x[1])))

fin_table <- fin_table %>% 
  mutate(ind = sapply(strsplit(fin_table$indicator, split='_', fixed=TRUE),function(x) (x[2])))

t <- group_by(fin_table, behavior, ind)

t <- summarise(t, value.mean = mean(value, na.rm = TRUE))

t <- t %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = value.mean)

t <- t %>% 
  mutate(hrank = hrank/6)
```

```{r, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
# Function by Greg Lin
# Notice bias here = a positive number. 
# Higher values give more widely spaced colors at the high end

make_color_pal <- function(colors, bias = 1) {
  get_color <- colorRamp(colors, bias = bias)
  function(x) rgb(get_color(x), maxColorValue = 255)
}

good_color <- make_color_pal(c("#ffffff", "#f2fbd2", "#c9ecb4", "#93d3ab", "#35b0ab"), bias = 2)

# Generate a vector of example numbers between 0 and 1
seq(0.1, 0.9, length.out = 12)
# [1] 0.1000000 0.1727273 0.2454545 0.3181818 0.3909091 0.4636364
# [7] 0.5363636 0.6090909 0.6818182 0.7545455 0.8272727 0.9000000
# create matching colors
good_color(seq(0.1, 0.9, length.out = 12))
# [1] "#E9F8CB" "#D9F2C0" "#C9ECB4" "#BDE6B2" "#B0E0AF" "#A4DAAD"
# [7] "#97D5AB" "#88CFAB" "#79C9AB" "#69C3AB" "#5ABDAB" "#4AB8AB"
# display the colors
seq(0.1, 0.9, length.out = 12) %>% 
  good_color() %>% 
  scales::show_col()
```

#### Boston Index

```{r, echo = FALSE, results = 'asis', message = FALSE}
### Boston Index (weighted by ZIP and age-sex-ethnicity)
t11 <- group_by(fin_table, behavior, ind)

t11 <- summarise(t11, w.mean = weighted.mean(value, wt, na.rm = TRUE))

t11 <- t11 %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = w.mean)

t11 <- t11 %>% 
  mutate(hrank = hrank/6)

# Rename columns
t11 <- t11 %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t11$Behavior[t11$Behavior == "ev"] <- "Purchase an EV"
t11$Behavior[t11$Behavior == "fly"] <- "Fly less*"
t11$Behavior[t11$Behavior == "offset"] <- "Purchase carbon offsets"
t11$Behavior[t11$Behavior == "recs"] <- "Purchase green energy"
t11$Behavior[t11$Behavior == "solar"] <- "Install solar panels"
t11$Behavior[t11$Behavior == "pbd"] <- "Eat less meat*"
t11$Behavior[t11$Behavior == "foodwaste"] <- "Waste less food*"

t11 <- t11 %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

tt = reactable(t11,
  style = list(fontSize = "12px"),
  defaultSortOrder = 'asc',
  defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = TRUE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center",
      minWidth = 100),
  # Add theme for the top border
    theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )
    ),
  columns = list(
    Behavior = colDef(
      minWidth = 170,
      align = "left"),
    Adoption = colDef(
      style = function(value) {
    normalized <- (value - min(t11$Adoption)) / (max(t11$Adoption) - min(t11$Adoption))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    Intention = colDef(
      style = function(value) {
    normalized <- (value - min(t11$Intention)) / (max(t11$Intention) - min(t11$Intention))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `Belief that others are engaging in the behavior` = colDef(
      style = function(value) {
    normalized <- (value - min(t11$`Belief that others are engaging in the behavior`)) / (max(t11$`Belief that others are engaging in the behavior`) - min(t11$`Belief that others are engaging in the behavior`))
    color <- good_color(normalized)
    list(background = color)
  },
      name = "Others have adopted",
      format = colFormat(digits = 2)),
    `Belief that others should engage in the behavior` = colDef(
       style = function(value) {
    normalized <- (value - min(t11$`Belief that others should engage in the behavior`)) / (max(t11$`Belief that others should engage in the behavior`) - min(t11$`Belief that others should engage in the behavior`))
    color <- good_color(normalized)
    list(background = color)
  },
      name = "Others should adopt",
      format = colFormat(digits = 2)),
    `Belief that others think people should engage in the behavior` = colDef(
      style = function(value) {
    normalized <- (value - min(t11$`Belief that others think people should engage in the behavior`)) / (max(t11$`Belief that others think people should engage in the behavior`) - min(t11$`Belief that others think people should engage in the behavior`))
    color <- good_color(normalized)
    list(background = color)
  },
      name = "Others think people should adopt",
      format = colFormat(digits = 2),
      minWidth = 120),
    `Program interest` = colDef(
      style = function(value) {
    normalized <- (value - min(t11$`Program interest`)) / (max(t11$`Program interest`) - min(t11$`Program interest`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 70),
    `Carbon impact ranking` = colDef(
      format = colFormat(digits = 2))),
  
  columnGroups = list(
    colGroup(name = "Beliefs that...", columns = c("Belief that others are engaging in the behavior", "Belief that others should engage in the behavior", "Belief that others think people should engage in the behavior"))))

div(
  class = "Behavior",
  div(
    # this can be called with CSS now via .title
    #class = "title",
    #h2("MIP Index: Boston"),
    "The survey was fielded from March 31 – April 21, 2021, drawing on the stratified sample of the Boston CBSA (n = 1,155)
    "
  ),
  # The actual table
  tt)
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE}
### Boston Index Unweighted
# Rename columns
t <- t %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t$Behavior[t$Behavior == "ev"] <- "Purchase an EV"
t$Behavior[t$Behavior == "fly"] <- "Fly less*"
t$Behavior[t$Behavior == "offset"] <- "Purchase carbon offsets"
t$Behavior[t$Behavior == "recs"] <- "Purchase green energy"
t$Behavior[t$Behavior == "solar"] <- "Install solar panels"
t$Behavior[t$Behavior == "pbd"] <- "Eat less meat*"
t$Behavior[t$Behavior == "foodwaste"] <- "Waste less food*"

t <- t %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

reactable(t,
  columns = list(Adoption = colDef(format = colFormat(digits = 2), minWidth = 90),
                 Intention = colDef(format = colFormat(digits = 2), minWidth = 90),
                 `Belief that others are engaging in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others think people should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Program interest` = colDef(format = colFormat(digits = 2)),
                 `Carbon impact ranking` = colDef(format = colFormat(digits = 2))),
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
### Boston Index Demo Weighted
t1 <- group_by(fin_table, behavior, ind)

t1 <- summarise(t1, w.mean = weighted.mean(value, demo_weight, na.rm = TRUE))

t1 <- t1 %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = w.mean)

t1 <- t1 %>% 
  mutate(hrank = hrank/6)
# Rename columns
t1 <- t1 %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t1$Behavior[t1$Behavior == "ev"] <- "Purchase an EV"
t1$Behavior[t1$Behavior == "fly"] <- "Fly less*"
t1$Behavior[t1$Behavior == "offset"] <- "Purchase carbon offsets"
t1$Behavior[t1$Behavior == "recs"] <- "Purchase green energy"
t1$Behavior[t1$Behavior == "solar"] <- "Install solar panels"
t1$Behavior[t1$Behavior == "pbd"] <- "Eat less meat*"
t1$Behavior[t1$Behavior == "foodwaste"] <- "Waste less food*"

t1 <- t1 %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

reactable(t1,
  columns = list(Adoption = colDef(format = colFormat(digits = 2), minWidth = 90),
                 Intention = colDef(format = colFormat(digits = 2), minWidth = 90),
                 `Belief that others are engaging in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others think people should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Program interest` = colDef(format = colFormat(digits = 2)),
                 `Carbon impact ranking` = colDef(format = colFormat(digits = 2))),
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))
```

```{r, echo = FALSE, include = FALSE, results = 'asis', message = FALSE, eval = FALSE}
### Boston Index ZIP weighted
t2 <- group_by(fin_table, behavior, ind)

t2 <- summarise(t2, w.mean = weighted.mean(value, zip.weight, na.rm = TRUE))

t2 <- t2 %>% 
  group_by(behavior) %>% 
  pivot_wider(names_from = ind, values_from = w.mean)

t2 <- t2 %>% 
  mutate(hrank = hrank/6)

# Rename columns
t2 <- t2 %>% 
  rename('Behavior' = behavior,
         'Adoption' = adoption,
         'Intention' = intent,
         'Belief that others are engaging in the behavior' = ee,
         'Belief that others should engage in the behavior' = pnb,
         'Belief that others think people should engage in the behavior' = ne,
         'Program interest' = program,
         'Carbon impact ranking' = hrank)

# Rename rows
t2$Behavior[t2$Behavior == "ev"] <- "Purchase an EV"
t2$Behavior[t2$Behavior == "fly"] <- "Fly less*"
t2$Behavior[t2$Behavior == "offset"] <- "Purchase carbon offsets"
t2$Behavior[t2$Behavior == "recs"] <- "Purchase green energy"
t2$Behavior[t2$Behavior == "solar"] <- "Install solar panels"
t2$Behavior[t2$Behavior == "pbd"] <- "Eat less meat*"
t2$Behavior[t2$Behavior == "foodwaste"] <- "Waste less food*"

t2 <- t2 %>% 
  select(Behavior, Adoption, Intention, `Belief that others are engaging in the behavior`, `Belief that others should engage in the behavior`, `Belief that others think people should engage in the behavior`, `Program interest`, `Carbon impact ranking`)

reactable(t2,
  columns = list(Adoption = colDef(format = colFormat(digits = 2), minWidth = 90),
                 Intention = colDef(format = colFormat(digits = 2), minWidth = 90),
                 `Belief that others are engaging in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Belief that others think people should engage in the behavior` = colDef(format = colFormat(digits = 2), minWidth = 140),
                 `Program interest` = colDef(format = colFormat(digits = 2)),
                 `Carbon impact ranking` = colDef(format = colFormat(digits = 2))),
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))
```

For eating less meat, flying less, and reducing food waste, adoption variable measured current attempt, rather than reported adoption (e.g., *Are you trying to fly less frequently than you used to?*)

#### Carbon Impact Ranking

The table below presents the average ranking in terms of the carbon mitigation potential of MIP (highlighted) and low-impact behaviors assigned by participants. For example, on average, installing rooftop solar was assigned rank 4.61 out of 12.

```{r, echo = FALSE, results = 'asis', message = FALSE, fig.align = 'center'}
#Ranking table
ranking_table <- index %>% 
  select(Vrid, offset_hrank:pack_lrank) %>% 
  pivot_longer(
   cols = ends_with(c("rank")),
   names_to = "behavior",
   values_to = "value",
   values_drop_na = TRUE) %>%
  group_by(behavior) %>% 
  summarise(mean = mean(value))

# Rename columns
ranking_table <- ranking_table %>% 
  rename('Behavior' = behavior,
         'Average position' = mean)

# Rename rows
ranking_table$Behavior[ranking_table$Behavior == "solar_hrank"] <- "Get 100% of electricity from solar panels on the roof instead of from the grid for one year"
ranking_table$Behavior[ranking_table$Behavior == "recycling_lrank"] <- "Recycle 100% of recyclable materials generated as waste, including newspaper, magazines, glass, plastic, and metal for one year"
ranking_table$Behavior[ranking_table$Behavior == "recs_hrank"] <- "Purchase 100% of household energy from renewable sources for one year"
ranking_table$Behavior[ranking_table$Behavior == "ev_hrank"] <- "Drive a fully electric car for one year"
ranking_table$Behavior[ranking_table$Behavior == "trees_lrank"] <- "Plant 10 trees"
ranking_table$Behavior[ranking_table$Behavior == "bulbs_lrank"] <- "Replace 25 incandescent light bulbs with ENERGY STAR lights"
ranking_table$Behavior[ranking_table$Behavior == "fridge_lrank"] <- "Replace old refrigerator with ENERGY STAR refrigerator"
ranking_table$Behavior[ranking_table$Behavior == "offset_hrank"] <- "Purchase carbon offsets to offset average American’s annual carbon footprint"
ranking_table$Behavior[ranking_table$Behavior == "pack_lrank"] <- "Eliminate all food packaging for one year"
ranking_table$Behavior[ranking_table$Behavior == "local_lrank"] <- "Source all of food locally for one year"
ranking_table$Behavior[ranking_table$Behavior == "fly_hrank"] <- "Take one fewer round-trip flight"
ranking_table$Behavior[ranking_table$Behavior == "pbd_hrank"] <- "Avoid eating all meat for one year"

ranking_t = reactable(ranking_table,
  style = list(fontSize = "12px"),
  defaultPageSize = 12,
  defaultSortOrder = 'asc',
  defaultSorted = 'Average position',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = FALSE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = FALSE,
    # apply defaults
    # 100 px and align to center of column
    defaultColDef = colDef(
      align = "center",
      minWidth = 100),
  # Add theme for the top border
    theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )
    ),
  columns = list(
    Behavior = colDef(
      minWidth = 490,
      align = "left"),
    `Average position` = colDef(
      name = "Average position",
      format = colFormat(digits = 2),
      maxWidth = 100)),
  rowStyle = function(index) {
  if (index == 2 | index == 3 | index == 6 | index == 8 |index == 9| index == 11) list(background = "#E9F8CB")
})

ranking_t
```

```{r, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
ev_cols <- c("EV: PI", "EV: Intent", "EV: Beliefs that others have adopted", "Beliefs that others should drive an EV", "Beliefs that others think people should drive an EV")



#social_cols <- c("EV: Beliefs that others have adopted", "EV: Beliefs that others should adopt", "EV: Beliefs that others think people should adopt")

BuYlRd <- function(x) rgb(colorRamp(c("#7fb7d7", "#ffffbf", "#fc8d59"))(x), maxColorValue = 255)
```

#### Correlation tables

```{r, echo = FALSE, results = 'asis', message = FALSE, fig.align = 'center', warning = FALSE, include = FALSE}
#Corr between intention to adopt and program interest 
cor_table_1 <- data %>% 
  select(
  #Vrid,
  #var13, #RID
  #EV
  var94, #intent
  var96, #program interest
  #Fly
  var97, #intent
  var98, #program interest
  #Offsets
  var99, #intent
  var100, #program interest
  #PBD
  var103, #intent
  var104, #program interest
  #RECs
  var105, #intent
  var106, #program interest
  #Solar
  var107, #intent
  var108, #program interest
  #Food waste
  var109, #intent
  var110 #program interest
  ) %>% 
  rename(
  #EV
  "I: EV" = var94,
  "PI: EV" = var96,
  #Fly
  "I: Fly" = var97,
  "PI: Fly" = var98,
  #Offset
  "PI: Offsets" = var100, #program interest
  "I: Offsets" = var99,
  #PBD
  "PI: PBD" = var104, #program interest
  "I: PBD" = var103, 
  #RECs
  "PI: RECs" = var106, #program interest
  "I: RECs" = var105,
  #Solar
  "PI: Solar" = var108, #program interest
  "I: Solar" = var107,
  #Food waste
  "PI: Food Waste" = var110, #program interest
  "I: Food Waste" = var109)

res <- cor(cor_table_1)
res <- round(res, 2)
res <- as.data.frame(res)
#upper.tri(res, diag = FALSE)
#upper <- res
#upper[upper.tri(res)] <- ""
#upper < -as.data.frame(res)
#upper

res_table1 <- reactable(res,
  style = list(fontSize = "11px"),
  defaultPageSize = 14,
  #defaultSortOrder = 'asc',
  #defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = TRUE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # Add theme for the top border
    theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )
    ),
  columns = list(
    `I: EV` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`I: EV`)) / (max(res$`I: EV`) - min(res$`I: EV`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `PI: EV` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`PI: EV`)) / (max(res$`PI: EV`) - min(res$`PI: EV`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `I: Fly` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`I: Fly`)) / (max(res$`I: Fly`) - min(res$`I: Fly`))
    color <- good_color(normalized)
    list(background = color)
  },
  maxWidth = 65,
      format = colFormat(digits = 2)),
    `PI: Fly` = colDef(
       style = function(value) {
    normalized <- (value - min(res$`PI: Fly`)) / (max(res$`PI: Fly`) - min(res$`PI: Fly`))
    color <- good_color(normalized)
    list(background = color)
  },
      maxWidth = 65,
      format = colFormat(digits = 2)),
    `I: Solar` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`I: Solar`)) / (max(res$`I: Solar`) - min(res$`I: Solar`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `PI: Solar` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`PI: Solar`)) / (max(res$`PI: Solar`) - min(res$`PI: Solar`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `I: Offsets` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`I: Offsets`)) / (max(res$`I: Offsets`) - min(res$`I: Offsets`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `PI: Offsets` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`PI: Offsets`)) / (max(res$`PI: Offsets`) - min(res$`PI: Offsets`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 70),
    `I: PBD` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`I: PBD`)) / (max(res$`I: PBD`) - min(res$`I: PBD`))
    color <- good_color(normalized)
    list(background = color)
  },
      maxWidth = 65,
      format = colFormat(digits = 2)),
    `PI: PBD` = colDef(
       style = function(value) {
    normalized <- (value - min(res$`PI: PBD`)) / (max(res$`PI: PBD`) - min(res$`PI: PBD`))
    color <- good_color(normalized)
    list(background = color)
  },
      maxWidth = 65,
      format = colFormat(digits = 2)),
    `I: RECs` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`I: RECs`)) / (max(res$`I: RECs`) - min(res$`I: RECs`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
    `PI: RECs` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`PI: RECs`)) / (max(res$`PI: RECs`) - min(res$`PI: RECs`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 65),
      `I: Food Waste` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`I: Food Waste`)) / (max(res$`I: Food Waste`) - min(res$`I: Food Waste`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 90),
    `PI: Food Waste` = colDef(
      style = function(value) {
    normalized <- (value - min(res$`PI: Food Waste`)) / (max(res$`PI: Food Waste`) - min(res$`PI: Food Waste`))
    color <- good_color(normalized)
    list(background = color)
  },
      format = colFormat(digits = 2),
      maxWidth = 95)))

res_table1
```

##### Pearson correlations between reported intention to engage in the behaviors

```{r, echo = FALSE, results = 'asis', message = FALSE, fig.align = 'center', warning = FALSE}
#Corr between intention to adopt and program interest 
intention_table <- data %>% 
  select(
  #Vrid,
  #var13, #RID
  #EV
  var94, #intent
  #Fly
  var97, #intent
  #Offsets
  var99, #intent
  #PBD
  var103, #intent
  #RECs
  var105, #intent
  #Solar
  var107, #intent
  #Food waste
  var109, #intent
  ) %>% 
  rename(
  #EV
  "Intention to drive an EV" = var94,
  #Fly
  "Intention to fly less" = var97,
  #Offset
  "Intention to buy offsets" = var99,
  #PBD
  "Intention to eat less meat" = var103, 
  #RECs
  "Intention to contract for green energy" = var105,
  #Solar
  "Intention to install solar" = var107,
  #Food waste
  "Intention to reduce food waste" = var109)

intention_table <- cor(intention_table)
intention_table <- round(intention_table, 2)
intention_table <- as.data.frame(intention_table)

intention_reactable = reactable(intention_table,
  defaultColDef = colDef(
    style = function(value) {
      if (!is.numeric(value)) return()
      normalized <- (value - min(intention_table)) / (max(intention_table) - min(intention_table))
      color <- BuYlRd(normalized)
      list(background = color)
    },
    format = colFormat(digits = 2),
  ),
  style = list(fontSize = "11px"),
  defaultPageSize = 30,
  #defaultSortOrder = 'asc',
  #defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = TRUE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # Add theme for the top border
  theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )))

intention_reactable
```

##### Pearson correlations between interest in programs that help adopt the behaviors

```{r, echo = FALSE, results = 'asis', message = FALSE, fig.align = 'center', warning = FALSE}
#Corr between intention to adopt and program interest 
interest_table <- data %>% 
  select(
  #Vrid,
  #var13, #RID
  #EV
  var96, #program interest
  #Fly
  var98, #program interest
  #Offsets
  var100, #program interest
  #PBD
  var104, #program interest
  #RECs
  var106, #program interest
  #Solar
  var108, #program interest
  #Food waste
  var110 #program interest
  ) %>% 
  rename(
  #EV
  "Interest in EV program" = var96,
  #Fly
  "Interest in fly less program" = var98,
  #Offset
  "Interest in offsets program" = var100, #program interest
  #PBD
  "Interest in eat less meat program" = var104, #program interest
  #RECs
  "Interest in green energy program" = var106, #program interest
  #Solar
  "Interest in solar program" = var108, #program interest
  #Food waste
  "Interest in reducing food waste program" = var110)

interest_table <- cor(interest_table)
interest_table <- round(interest_table, 2)
interest_table <- as.data.frame(interest_table)

interest_reactable = reactable(interest_table,
  defaultColDef = colDef(
    style = function(value) {
      if (!is.numeric(value)) return()
      normalized <- (value - min(interest_table)) / (max(interest_table) - min(interest_table))
      color <- BuYlRd(normalized)
      list(background = color)
    },
    format = colFormat(digits = 2),
  ),
  style = list(fontSize = "11px"),
  defaultPageSize = 30,
  #defaultSortOrder = 'asc',
  #defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = TRUE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # Add theme for the top border
  theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )))

interest_reactable
```

##### Pearson correlations between demographic and psychographic predictors and behavior-related variables

```{r, echo = FALSE, results = 'asis', message = FALSE, fig.align = 'center', warning = FALSE}
#Corr table 2
corr_table_2 <- data %>% 
  select(
  #wt,
  #Vrid,
  #var13, #RID
  #EV
  #var26, #adoption
  var87, #EE
  var28, #PNB,
  var88, #NE
  var94, #intent
  var96, #program interest
  #Fly
  #var70, #Are you trying to fly less frequently than you used to?
  var69, #EE
  var38, #PNB
  var35, #NE
  var97, #intent
  var98, #program interest
  #Offsets
  #var39, #adoption
  var40, #EE
  var41, #PNB
  var42, #NE
  var99, #intent
  var100, #program interest
  #PBD
  #var71, #Are you trying to eat less meat than you used to?
  #var115, #adoption % of meals
  var72, #EE
  var66, #PNB
  var48, #NE
  var103, #intent
  var104, #program interest
  #RECs
  #var54, #adoption
  var55, #EE
  var56, #PNB
  var57, #NE
  var105, #intent
  var106, #program interest
  #Solar
  #var59, #adoption
  var60, #EE
  var61, #PNB
  var62, #NE
  var107, #intent
  var108, #program interest
  #Food waste
  #var73, #Are you currently trying to reduce the amount of food waste you produce?
  var74, #EE
  var75, #PNB
  var76, #NE
  var109, #intent
  var110, #program interest
  #demographics
  age_group,
  sex,
  ethnicity,
  var20, #politics
  var19, #income
  var17, #education
  #employment info
  var92, #empl status
  var93, #empl sector
  var102, #empl size
  #social participation & donation
  var118O832:var119O841) %>% 
  rename(
  #EV
  #ev_adoption = var26,
  ev_ee = var87,
  ev_pnb = var28,
  ev_ne = var88,
  ev_intent = var94,
  ev_program_interest = var96,
  #Fly
  #fly_adoption = var70, #trying to fly less
  fly_ee = var69, #EE
  fly_pnb = var38, #PNB
  fly_ne = var35, #NE
  fly_intent = var97,
  fly_program_interest = var98,
  #Offset
  #offset_adoption = var39, #adoption
  offset_ee = var40, #EE
  offset_pnb = var41, #PNB
  offset_ne = var42, #NE
  offset_program_interest = var100, #program interest
  offset_intent = var99,
  #PBD
  #pbd_adoption = var71, #trying to
  pbd_ee = var72, #EE
  pbd_pnb = var66, #PNB
  pbd_ne = var48, #NE
  pbd_program_interest = var104, #program interest
  pbd_intent = var103, 
  #RECs
  #recs_adoption = var54, #adoption
  recs_ee = var55, #EE
  recs_pnb = var56, #PNB
  recs_ne = var57, #NE
  recs_program_interest = var106, #program interest
  recs_intent = var105,
  #Solar
  #solar_adoption = var59, #adoption
  solar_ee = var60, #EE
  solar_pnb = var61, #PNB
  solar_ne = var62, #NE
  solar_program_interest = var108, #program interest
  solar_intent = var107,
  #Food waste
  #foodwaste_adoption = var73, #attempt
  foodwaste_ee = var74, #EE
  foodwaste_pnb = var75, #PNB
  foodwaste_ne = var76, #NE
  foodwaste_program_interest = var110, #program interest
  foodwaste_intent = var109,
  #dem
  politics = var20,
  income = var19, 
  education = var17,
  #employment info
  employment_status = var92, #empl status
  employment_sector = var93, #empl sector
  company_size = var102, #empl size
  #social participation
  part_religion = var118O832,
  part_school = var118O833,
  part_alumni = var118O834,
  part_neighbor = var118O835,
  part_none = var118O836,
  #social donation
  donation_religion = var119O837,
  donation_school = var119O838,
  donation_alumni = var119O839,
  donation_neighbor = var119O840,
  donate_none = var119O841) 

corr_table_2 <- dummy_cols(corr_table_2, select_columns = c("sex", "ethnicity", "age_group", "employment_status", "employment_sector"))

corr_table_2 <- data.frame(lapply(corr_table_2, function(x) as.numeric(as.character(x))))

corr_table_2 <- corr_table_2 %>% 
  select(ev_ee:foodwaste_program_interest, politics:education, company_size:age_group_65.:employment_status_10792, employment_sector_10492, employment_sector_10496, employment_sector_10499)

corr_table_2 <- corr_table_2 %>% 
  mutate(
    income = case_when(income == 10063 ~ 11, TRUE ~ income))

res.cor2 <- correlate(corr_table_2)

res.cor2$term[res.cor2$term == "income"] <- "Household income"
res.cor2$term[res.cor2$term == "age_group_18.24"] <- "Age: 18-24"
res.cor2$term[res.cor2$term == "age_group_25.34"] <- "Age: 25-34"
res.cor2$term[res.cor2$term == "age_group_35.44"] <- "Age: 35-44"
res.cor2$term[res.cor2$term == "age_group_45.54"] <- "Age: 45-54"
res.cor2$term[res.cor2$term == "age_group_55.64"] <- "Age: 55-64"
res.cor2$term[res.cor2$term == "age_group_65."] <- "Age: 65+"
res.cor2$term[res.cor2$term == "sex_Female"] <- "Female"
res.cor2$term[res.cor2$term == "sex_Male"] <- "Male"

res.cor2$term[res.cor2$term == "ethnicity_White"] <- "Ethnicity: White"
res.cor2$term[res.cor2$term == "ethnicity_Black"] <- "Ethnicity: Black"
res.cor2$term[res.cor2$term == "ethnicity_Asian"] <- "Ethnicity: Asian"
res.cor2$term[res.cor2$term == "ethnicity_Other"] <- "Ethnicity: Other"

res.cor2$term[res.cor2$term == "education"] <- "Education level"
res.cor2$term[res.cor2$term == "politics"] <- "Political orientation: Conservative"

res.cor2$term[res.cor2$term == "employment_status_10485"] <- "Employed"
res.cor2$term[res.cor2$term == "employment_status_10792"] <- "Retired"
res.cor2$term[res.cor2$term == "employment_status_10487"] <- "Unemployed"

res.cor2$term[res.cor2$term == "company_size"] <- "Employer size"
res.cor2$term[res.cor2$term == "employment_sector_10499"] <- "Industry: Technology/ Software"
res.cor2$term[res.cor2$term == "employment_sector_10496"] <- "Industry: Healthcare"
res.cor2$term[res.cor2$term == "employment_sector_10492"] <- "Industry: Education"

res.cor2$term[res.cor2$term == "part_religion"] <- "Participation: Religious Group"
res.cor2$term[res.cor2$term == "part_school"] <- "Participation: School Association"
res.cor2$term[res.cor2$term == "part_alumni"] <- "Participation: Alumni Group"
res.cor2$term[res.cor2$term == "part_neighbor"] <- "Participation: Neighborhood Org"

res.cor2$term[res.cor2$term == "donation_religion"] <- "Past Donation: Religious Group"
res.cor2$term[res.cor2$term == "donation_school"] <- "Past Donation: School Association"
res.cor2$term[res.cor2$term == "donation_alumni"] <- "Past Donation: Alumni Group"
res.cor2$term[res.cor2$term == "donation_neighbor"] <- "Past Donation: Neighborhood Org"

res.cor2 <- res.cor2 %>% mutate_if(is.numeric, round, digits = 2)

res.cor2[is.na(res.cor2)] <- 0

x2 <- c("Age: 18-24", "Age: 25-34", "Age: 35-44", "Age: 45-54", "Age: 55-64", "Age: 65+",
        "Female", "Male", 
        "Ethnicity: White", "Ethnicity: Black", "Ethnicity: Asian", "Ethnicity: Other", "Household income", "Education level", "Political orientation: Conservative", 
        "Employed", "Retired", "Unemployed", "Company Size", "Industry: Technology/ Software", "Industry: Healthcare", "Industry: Education", 
        "Participation: Religious Group", "Participation: School Association", "Participation: Alumni Group", "Participation: Neighborhood Org", "Past Donation: Religious Group", "Past Donation: School Association", "Past Donation: Alumni Group", "Past Donation: Neighborhood Org")

tt3 = res.cor2 %>% 
  focus(ev_program_interest, ev_intent, ev_ee, ev_pnb, ev_ne,
        solar_program_interest, solar_intent, solar_ee, solar_pnb, solar_ne,
        recs_program_interest, recs_intent, recs_ee, recs_pnb, recs_ne,
        offset_program_interest, offset_intent, offset_ee, offset_pnb, offset_ne,
        fly_program_interest, fly_intent, fly_ee, fly_pnb, fly_ne, 
        pbd_program_interest, pbd_intent, pbd_ee, pbd_pnb, pbd_ne,
        foodwaste_program_interest, foodwaste_intent, foodwaste_ee, foodwaste_pnb, foodwaste_ne) %>% 
  rename('Predictor' = term,
         'Interest in EV program' = ev_program_interest,
         'Intention to buy an EV' = ev_intent,
         'Beliefs that others drive an EV' = ev_ee,
         'Beliefs that others should drive an EV' = ev_pnb,
         'Beliefs that others think people should drive an EV' = ev_ne,
         'Interest in solar program' = solar_program_interest,
         'Intention to install solar' = solar_intent,
         'Beliefs that others have solar' = solar_ee,
         'Beliefs that others should install solar' = solar_pnb,
         'Beliefs that others think people should install solar' = solar_ne,
         'Interest in green energy program' = recs_program_interest,
         'Intention to contract for green energy' = recs_intent,
         'Beliefs that others have green energy' = recs_ee,
         'Beliefs that others should have green energy' = recs_pnb,
         'Beliefs that others think people should have green energy' = recs_ne,
         'Interest in offsets program' = offset_program_interest,
         'Intention to buy offsets' = offset_intent,
         'Beliefs that others bought offsets' = offset_ee,
         'Beliefs that others should buy offsets' = offset_pnb,
         'Beliefs that others think people should buy offsets' = offset_ne,
         'Interest in flying less program' = fly_program_interest,
         'Intention to fly less' = fly_intent,
         'Beliefs that others are flying less' = fly_ee,
         'Beliefs that others should fly less' = fly_pnb,
         'Beliefs that others think people should fly less' = fly_ne,
         'Interest in eating less meat program' = pbd_program_interest,
         'Intention to eat less meat' = pbd_intent,
         'Beliefs that others eat less meat' = pbd_ee,
         'Beliefs that others should eat less meat' = pbd_pnb,
         'Beliefs that others think people should eat less meat' = pbd_ne,
         'Interest in reducing food waste program' = foodwaste_program_interest,
         'Intention to reduce food waste' = foodwaste_intent,
         'Beliefs that others reduce food waste' = foodwaste_ee,
         'Beliefs that others should reduce food waste' = foodwaste_pnb,
         'Beliefs that others think people should reduce food waste' = foodwaste_ne) %>%
  slice(match(x2, Predictor)) #%>% #reorder predictors

sticky_style <- list(position = "sticky", left = 0, background = "#fff", zIndex = 1,
                     borderRight = "1px solid #eee")

tt5 = reactable(tt3,
                height = 500,
  defaultColDef = colDef(
    footer = function(values, name) htmltools::div(name, style = list(fontWeight = 600)),
    style = function(value) {
      if (!is.numeric(value)) return()
      normalized <- (value - min(tt3[-1])) / (max(tt3[-1]) - min(tt3[-1]))
      color <- BuYlRd(normalized)
      list(background = color)
    },
    format = colFormat(digits = 2),
  ),
  style = list(fontSize = "11px"),
  defaultPageSize = 30,
  #defaultSortOrder = 'asc',
  #defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = TRUE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # Add theme for the top border
  columns = list(
  `Predictor` =  colDef(
      style = sticky_style,
      headerStyle = sticky_style,
      minWidth = 120),
  `Beliefs that others think people should drive an EV` = colDef(
minWidth = 120),
    `Beliefs that others think people should install solar` = colDef(
minWidth = 120),
    `Beliefs that others think people should have green energy` = colDef(
      minWidth = 120),
    `Beliefs that others think people should eat less meat` = colDef(
minWidth = 120),
    `Beliefs that others think people should reduce food waste` = colDef(
      minWidth = 120)
  ),  
  theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )))

tt5
```

```{r, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, eval = FALSE}
### 

tt4 = reactable(tt3,
                columns = list(
    `EV: PI` = colDef(
      name = "Program interest",
      style = function(value) {
    normalized <- (value - min(tt3$`EV: PI`)) / (max(tt3$`EV: PI`) - min(tt3$`EV: PI`))
    color <- BuYlRd(normalized)
    list(background = color)
  }),
  `EV: Intent` = colDef(
    name = "Intention",
    style = function(value) {
    normalized <- (value - min(tt3$`EV: Intent`)) / (max(tt3$`EV: Intent`) - min(tt3$`EV: Intent`))
    color <- BuYlRd(normalized)
    list(background = color)
  }),
  `EV: Beliefs that others have adopted` = colDef(
    name = "Beliefs that others drive an EV",
    style = function(value) {
    normalized <- (value - min(tt3$`EV: Beliefs that others have adopted`)) / (max(tt3$`EV: Beliefs that others have adopted`) - min(tt3$`EV: Beliefs that others have adopted`))
    color <- BuYlRd(normalized)
    list(background = color)
  }),
  `Solar: PI` = colDef(style = function(value) {
    normalized <- (value - min(tt3$`Solar: PI`)) / (max(tt3$`Solar: PI`) - min(tt3$`Solar: PI`))
    color <- BuYlRd(normalized)
    list(background = color)
  }),
  `Solar: Intent` = colDef(style = function(value) {
    normalized <- (value - min(tt3$`Solar: Intent`)) / (max(tt3$`Solar: Intent`) - min(tt3$`Solar: Intent`))
    color <- BuYlRd(normalized)
    list(background = color)
  }),
  `Solar: Beliefs that others have adopted` = colDef(style = function(value) {
    normalized <- (value - min(tt3$`Solar: Beliefs that others have adopted`)) / (max(tt3$`Solar: Beliefs that others have adopted`) - min(tt3$`Solar: Beliefs that others have adopted`))
    color <- BuYlRd(normalized)
    list(background = color)
  })
  ),
  style = list(fontSize = "11px"),
  defaultPageSize = 30,
  #defaultSortOrder = 'asc',
  #defaultSorted = 'Behavior',
  showSortIcon = FALSE,
  # ALL one page option (no scrolling or page swapping)
    pagination = TRUE,
    # compact for an overall smaller table width wise
    compact = TRUE,
    # borderless - TRUE or FALSE
    borderless = FALSE,
    # Stripes - TRUE or FALSE
    striped = TRUE,
    highlight = TRUE,  
  # fullWidth - either fit to width or not
    fullWidth = TRUE,
    # Add theme for the top border
    theme = reactableTheme(
      headerStyle = list(
        "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
        "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
        borderColor = "#555"
      )
    ),
   columnGroups = list(
    colGroup(name = "Electric Vehicles", columns = c("Program interest", "Intention", "EV: Beliefs that others have adopted", "EV: Beliefs that others should adopt", "EV: Beliefs that others think people should adopt")))) 

tt4
```

```{r, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
library(jtools)
options("jtools-digits" = 6)
reg <- data %>% 
  select(
  wt,
  #Vrid,
  #var13, #RID
  #EV
  #var26, #adoption
  var87, #EE
  var28, #PNB,
  var88, #NE
  var94, #intent
  var96, #program interest
  #Fly
  #var70, #Are you trying to fly less frequently than you used to?
  var69, #EE
  var38, #PNB
  var35, #NE
  var97, #intent
  var98, #program interest
  #Offsets
  #var39, #adoption
  var40, #EE
  var41, #PNB
  var42, #NE
  var99, #intent
  var100, #program interest
  #PBD
  #var71, #Are you trying to eat less meat than you used to?
  #var115, #adoption % of meals
  var72, #EE
  var66, #PNB
  var48, #NE
  var103, #intent
  var104, #program interest
  #RECs
  #var54, #adoption
  var55, #EE
  var56, #PNB
  var57, #NE
  var105, #intent
  var106, #program interest
  #Solar
  #var59, #adoption
  var60, #EE
  var61, #PNB
  var62, #NE
  var107, #intent
  var108, #program interest
  #Food waste
  #var73, #Are you currently trying to reduce the amount of food waste you produce?
  var74, #EE
  var75, #PNB
  var76, #NE
  var109, #intent
  var110, #program interest
  #demographics
  age_group,
  sex,
  ethnicity,
  var20, #politics
  var19, #income
  var17, #education
  ) %>% 
  rename(
  #EV
  #ev_adoption = var26,
  ev_ee = var87,
  ev_pnb = var28,
  ev_ne = var88,
  ev_intent = var94,
  ev_program_interest = var96,
  #Fly
  #fly_adoption = var70, #trying to fly less
  fly_ee = var69, #EE
  fly_pnb = var38, #PNB
  fly_ne = var35, #NE
  fly_intent = var97,
  fly_program_interest = var98,
  #Offset
  #offset_adoption = var39, #adoption
  offset_ee = var40, #EE
  offset_pnb = var41, #PNB
  offset_ne = var42, #NE
  offset_program_interest = var100, #program interest
  offset_intent = var99,
  #PBD
  #pbd_adoption = var71, #trying to
  pbd_ee = var72, #EE
  pbd_pnb = var66, #PNB
  pbd_ne = var48, #NE
  pbd_program_interest = var104, #program interest
  pbd_intent = var103, 
  #RECs
  #recs_adoption = var54, #adoption
  recs_ee = var55, #EE
  recs_pnb = var56, #PNB
  recs_ne = var57, #NE
  recs_program_interest = var106, #program interest
  recs_intent = var105,
  #Solar
  #solar_adoption = var59, #adoption
  solar_ee = var60, #EE
  solar_pnb = var61, #PNB
  solar_ne = var62, #NE
  solar_program_interest = var108, #program interest
  solar_intent = var107,
  #Food waste
  #foodwaste_adoption = var73, #attempt
  foodwaste_ee = var74, #EE
  foodwaste_pnb = var75, #PNB
  foodwaste_ne = var76, #NE
  foodwaste_program_interest = var110, #program interest
  foodwaste_intent = var109,
  #dem
  politics = var20,
  income = var19, 
  education = var17) 

reg <- within(reg, ethnicity <- relevel(ethnicity, ref = "White"))
reg <- within(reg, age_group <- relevel(age_group, ref = "65+"))

reg <- reg %>% 
  mutate(
    income = as.numeric(income),
    income = case_when(income == 10063 ~ 11, TRUE ~ income))

reg$education_category = recode(reg$education, '1' = "No college degree", '2' = "No college degree", '3' = "No college degree", '4' = "College degree", '5' = "College degree", '6' = "Graduate degree")

reg$education_category <- as.factor(reg$education_category)

reg <- within(reg, education_category <- relevel(education_category, ref = "No college degree"))

reg$income_category = recode(reg$income, '1' = "Less than $29,000", '2' = "Less than $29,000", '3' = "$30,000 to $49,000", '4' = "$30,000 to $49,000", '5' = "$50,000 to $69,000", '6' = "$50,000 to $69,000", '7' = "$70,000 to $89,000", '8' = "$70,000 to $89,000", '9' = "$90,000 to $149,000", '10' = "$90,000 to $149,000", '11' = "$150,000 or more")

reg$income_category <- as.factor(reg$income_category)

reg <- within(reg, income_category <- relevel(income_category, ref = "Less than $29,000"))
```

```{r, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
ev_w <- reg %>% 
  lm(scale(ev_intent) ~ scale(ev_ee) + scale(ev_pnb) + scale(ev_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)


ev_d_w <- reg %>% 
  lm(scale(ev_intent) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

ev_d_w <- tidy(ev_d_w) %>% mutate(model = "EV_d_w")

ev_w1 <- tidy(ev_w) %>% 
  filter(!grepl('eth*', term), term != "scale(income)", term != "scale(education)", term != "age_group25-34", term != "age_group35-44", term != "age_group45-54", term != "age_group55-64", term != "age_group65+", term != "sexMale") %>% mutate(model = "EV_w")

ev_w1

ev_w2 <- tidy(ev_w) %>% mutate(model = "EV_w2")

summary(ev_w) 

solar_w <- reg %>% 
  lm(scale(solar_intent) ~ scale(solar_ee) + scale(solar_pnb) + scale(solar_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

solar_d_w <- reg %>%
    lm(scale(solar_intent) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)
  
solar_d_w <- tidy(solar_d_w) %>% mutate(model = "solar_d_w")


solar_w1 <- tidy(solar_w) %>% 
  filter(!grepl('eth*', term), term != "scale(income)", term != "scale(education)", term != "age_group25-34", term != "age_group35-44", term != "age_group45-54", term != "age_group55-64", term != "age_group65+", term != "sexMale") %>% mutate(model = "Solar_w")

solar_w2 <- tidy(solar_w) %>% mutate(model = "Solar_w2")

summary(solar_w)

offset_w <- reg %>% 
  lm(scale(offset_intent) ~ scale(offset_ee) + scale(offset_pnb) + scale(offset_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

offset_d_w <- reg %>% 
  lm(scale(offset_intent) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

offset_d_w <- tidy(offset_d_w) %>% mutate(model = "offset_d_w")


summary(offset_w)

offset_w1 <- tidy(offset_w) %>% 
  filter(!grepl('ethi*', term), term != "scale(income)", term != "scale(education)", term != "age_group25-34", term != "age_group35-44", term != "age_group45-54", term != "age_group55-64", term != "age_group65+", term != "sexMale") %>% mutate(model = "Offset_w")

summary(offset_w1)

offset_w2 <- tidy(offset_w) %>% mutate(model = "offset_w2")


recs_w <- reg %>% 
  lm(scale(recs_intent) ~ scale(recs_ee) + scale(recs_pnb) + scale(recs_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

recs_d_w <- reg %>% 
  lm(scale(recs_intent) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)



recs_d_w <- tidy(recs_d_w) %>% mutate(model = "recs_d_w")


recs_w1 <- tidy(recs_w) %>% 
  filter(!grepl('eth*', term), term != "scale(income)", term != "scale(education)", term != "age_group25-34", term != "age_group35-44", term != "age_group45-54", term != "age_group55-64", term != "age_group65+", term != "sexMale") %>% mutate(model = "RECs_w")

recs_w2 <- tidy(recs_w) %>% mutate(model = "recs_w2")


summary(recs_w)

fly_less_w <- reg %>% 
  lm(scale(fly_intent) ~ scale(fly_ee) + scale(fly_pnb) + scale(fly_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

fly_less_d_w <- reg %>% 
  lm(scale(fly_intent) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

fly_less_d_w <- tidy(fly_less_d_w) %>% mutate(model = "fly_less_d_w")


fly_less_w1 <- tidy(fly_less_w) %>% 
  filter(!grepl('eth*', term), term != "scale(income)", term != "scale(education)", term != "age_group25-34", term != "age_group35-44", term != "age_group45-54", term != "age_group55-64", term != "age_group65+", term != "sexMale") %>% mutate(model = "fly_less_w")

fly_less_w2 <- tidy(fly_less_w) %>% mutate(model = "fly_less_w2")


summary(fly_less_w)

pbd_w <- reg %>% 
  lm(scale(pbd_intent) ~ scale(pbd_ee) + scale(pbd_pnb) + scale(pbd_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

pbd_d_w <- reg %>% 
  lm(scale(pbd_intent) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

pbd_d_w <- tidy(pbd_d_w) %>% mutate(model = "pbd_d_w")


pbd_w_1 <- tidy(pbd_w) %>% 
  filter(!grepl('eth*', term), term != "scale(income)", term != "scale(education)", term != "age_group25-34", term != "age_group35-44", term != "age_group45-54", term != "age_group55-64", term != "age_group65+", term != "sexMale") %>% mutate(model = "pbd_w")

pbd_w2 <- tidy(pbd_w) %>% mutate(model = "pbd_w2")


summary(pbd_w)

food_waste_w <- reg %>% 
  lm(scale(foodwaste_intent) ~ scale(foodwaste_ee) + scale(foodwaste_pnb) + scale(foodwaste_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

food_waste_d_w <- reg %>% 
  lm(scale(foodwaste_intent) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

food_waste_d_w <- tidy(food_waste_d_w) %>% mutate(model = "food_waste_d_w")


food_waste_w1 <- tidy(food_waste_w) %>% 
  filter(!grepl('eth*', term), term != "scale(income)", term != "scale(education)", term != "age_group25-34", term != "age_group35-44", term != "age_group45-54", term != "age_group55-64", term != "age_group65+", term != "sexMale") %>% mutate(model = "food_waste_w")

food_waste_w2 <- tidy(food_waste_w) %>% mutate(model = "food_waste_w2")

summary(food_waste_w)
```

```{r, include = FALSE, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
# Program interest
ev_p <- reg %>% 
  lm(scale(ev_program_interest) ~ scale(ev_ee) + scale(ev_pnb) + scale(ev_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

ev_p <- tidy(ev_p) %>% mutate(model = "ev_p")

ev_p_d <- reg %>% 
  lm(scale(ev_program_interest) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

summary(ev_p_d)

ev_p_d <- tidy(ev_p_d) %>% mutate(model = "EV_p_d")

##

solar_p <- reg %>% 
  lm(scale(solar_program_interest) ~ scale(solar_ee) + scale(solar_pnb) + scale(solar_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

solar_p_d <- reg %>%
    lm(scale(solar_program_interest) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)
  
solar_p_d <- tidy(solar_p_d) %>% mutate(model = "solar_p_d")

solar_p <- tidy(solar_p) %>% mutate(model = "solar_p")

##

offset_p <- reg %>% 
  lm(scale(offset_program_interest) ~ scale(offset_ee) + scale(offset_pnb) + scale(offset_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

offset_p_d <- reg %>% 
  lm(scale(offset_program_interest) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

offset_p_d <- tidy(offset_p_d) %>% mutate(model = "offset_p_d")

offset_p <- tidy(offset_p) %>% mutate(model = "offset_p")

##

recs_p <- reg %>% 
  lm(scale(recs_program_interest) ~ scale(recs_ee) + scale(recs_pnb) + scale(recs_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

recs_p_d <- reg %>% 
  lm(scale(recs_program_interest) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

recs_p_d <- tidy(recs_p_d) %>% mutate(model = "recs_p_d")

recs_p <- tidy(recs_p) %>% mutate(model = "recs_p")

##

fly_less_p <- reg %>% 
  lm(scale(fly_program_interest) ~ scale(fly_ee) + scale(fly_pnb) + scale(fly_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

fly_less_p_d <- reg %>% 
  lm(scale(fly_program_interest) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

fly_less_p_d <- tidy(fly_less_p_d) %>% mutate(model = "fly_less_p_d")


fly_less_p <- tidy(fly_less_p) %>% mutate(model = "fly_less_p")

##

pbd_p <- reg %>% 
  lm(scale(pbd_program_interest) ~ scale(pbd_ee) + scale(pbd_pnb) + scale(pbd_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

pbd_p_d <- reg %>% 
  lm(scale(pbd_program_interest) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

pbd_p_d <- tidy(pbd_p_d) %>% mutate(model = "pbd_p_d")

pbd_p <- tidy(pbd_p) %>% mutate(model = "pbd_p")

##

food_waste_p <- reg %>% 
  lm(scale(foodwaste_program_interest) ~ scale(foodwaste_ee) + scale(foodwaste_pnb) + scale(foodwaste_ne) + scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

food_waste_p_d <- reg %>% 
  lm(scale(foodwaste_program_interest) ~ scale(politics) + income_category + education_category + age_group + sex + ethnicity, data =.)

food_waste_p_d <- tidy(food_waste_p_d) %>% mutate(model = "food_waste_p_d")

food_waste_p <- tidy(food_waste_p) %>% mutate(model = "food_waste_p")
```

```{r, include = FALSE, eval = FALSE}
ev_p_d1 <- reg %>% 
  lm(scale(ev_program_interest) ~ income_category, data =.)
summary(ev_p_d1)

ev_p_d2 <- reg %>% 
  lm(scale(ev_program_interest) ~ income_category + education_category, data =.)
summary(ev_p_d2)

ev_p_d3 <- reg %>% 
  lm(scale(ev_program_interest) ~ income_category + ethnicity, data =.)
summary(ev_p_d3)

ev_p_d4 <- reg %>% 
  lm(scale(ev_program_interest) ~ age_group, data =.)
summary(ev_p_d4)

+ education_category + age_group + sex + ethnicity

###

solar_p_d1 <- reg %>% 
  lm(scale(solar_program_interest) ~ income_category + education_category + ethnicity + sex + age_group, data =.)
summary(solar_p_d1)
summ(solar_p_d1, vifs = TRUE)
#summ(ev_p_d2, vifs = TRUE)

solar_p_d2 <- reg %>% 
  lm(scale(solar_program_interest) ~ education_category + income_category + age_group, data =.)
summary(solar_p_d2)

ev_p_d3 <- reg %>% 
  lm(scale(ev_program_interest) ~ income_category + ethnicity, data =.)
summary(ev_p_d3)

ev_p_d4 <- reg %>% 
  lm(scale(ev_program_interest) ~ age_group, data =.)
summary(ev_p_d4)

###


carbon_p_d <- reg %>% 
  lm(scale(offset_program_interest) ~ income_category + education_category, data =.)
summary(carbon_p_d)


## fly less

fly_p_d <- reg %>% 
  lm(scale(fly_program_interest) ~ education_category + income_category + sex, data =.)
summary(fly_p_d)

## reduce food waste

food_waste_p_d <- reg %>% 
  lm(scale(foodwaste_program_interest) ~ sex + ethnicity, data =.)
summary(food_waste_p_d)


### pbd

pbd_program <- reg %>% 
  lm(scale(pbd_program_interest) ~ ethnicity, data =.)
summary(pbd_program)


## correlations between demographics

corr_table_3 <- corr_table_2 %>% 
  select(education, income, sex_Female, sex_Male, ethnicity_Asian:age_group_65.)

res.cor2 <- correlate(corr_table_3)

res.cor2$term[res.cor2$term == "income"] <- "Household income"
res.cor2$term[res.cor2$term == "age_group_18.24"] <- "Age: 18-24"
res.cor2$term[res.cor2$term == "age_group_25.34"] <- "Age: 25-34"
res.cor2$term[res.cor2$term == "age_group_35.44"] <- "Age: 35-44"
res.cor2$term[res.cor2$term == "age_group_45.54"] <- "Age: 45-54"
res.cor2$term[res.cor2$term == "age_group_55.64"] <- "Age: 55-64"
res.cor2$term[res.cor2$term == "age_group_65."] <- "Age: 65+"
res.cor2$term[res.cor2$term == "sex_Female"] <- "Female"
res.cor2$term[res.cor2$term == "sex_Male"] <- "Male"

res.cor2$term[res.cor2$term == "ethnicity_White"] <- "Ethnicity: White"
res.cor2$term[res.cor2$term == "ethnicity_Black"] <- "Ethnicity: Black"
res.cor2$term[res.cor2$term == "ethnicity_Asian"] <- "Ethnicity: Asian"
res.cor2$term[res.cor2$term == "ethnicity_Other"] <- "Ethnicity: Other"

res.cor2$term[res.cor2$term == "education"] <- "Education level"
#res.cor2$term[res.cor2$term == "politics"] <- "Political orientation: Conservative"
```

```{r, eval = FALSE, include = FALSE}
reg1 <- reg %>% 
  select(fly_program_interest, sex, age_group, income_category, politics, education_category, ethnicity)

# Create variables 
x_vars = model.matrix(fly_program_interest~., reg1)[ ,-1] # remove DV, leave only predictors
y_var = reg1$fly_program_interest
lam = 10^seq(2,-2, by = -.1)

# Create a test/train sample split (equal split)
set.seed(1)
train = sample(1:nrow(x_vars),nrow(x_vars)/(2))
x_test = reg1[-train, ]
y_test = x_test$fly_program_interest

library(glmnet)

# Identify the best lambda
cv_output = cv.glmnet(x_vars[train, ], y_var[train],
                      alpha= 1, lambda = lam)
best_lam = cv_output$lambda.min
#best_lam


# Use the best lambda to train the LASSO model
lasso = glmnet(x_vars[train, ], y_var[train], 
               alpha=1, lambda = best_lam)

coef(lasso)
```

#### Plots of standardized regression coefficients from linear models regressing intention to perform each behavior/program interest on each of the listed covariates

```{r, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, fig.width = 9, fig.height = 5, include = FALSE}
# Use tibble dfs
models <- rbind(ev_w1, offset_w1, recs_w1, solar_w1, pbd_w_1, food_waste_w1, fly_less_w1)

# Create list of brackets (label, topmost included predictor, bottommost included predictor)
bracket <- list(c("Beliefs about ...", "Others' behavior", "What others' think \nshould be done"))

p <- {dwplot(models, 
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2), 
        # Customize the of appearance of the dots and whiskers
        dot_args = list(aes(shape = model)),
        whisker_args = list(aes(linetype = model))) %>%
    # Put models on one graph by assigning them to the same names
    relabel_predictors(c("scale(ev_ee)" = "Others' behavior",                  
                         "scale(ev_pnb)" = "What should be done", 
                         "scale(ev_ne)" = "What others' think \nshould be done", 
                         "scale(offset_ee)" = "Others' behavior",            
                         "scale(offset_pnb)" = "What should be done", 
                         "scale(offset_ne)" = "What others' think \nshould be done",
                         "scale(recs_ee)" = "Others' behavior",                 
                         "scale(recs_pnb)" = "What should be done", 
                         "scale(recs_ne)" = "What others' think \nshould be done",
                         "scale(solar_ee)" = "Others' behavior",                       
                         "scale(solar_pnb)" = "What should be done", 
                         "scale(solar_ne)" = "What others' think \nshould be done",
                         "scale(foodwaste_ee)" = "Others' behavior",            
                         "scale(foodwaste_pnb)" = "What should be done", 
                         "scale(foodwaste_ne)" = "What others' think \nshould be done",
                         "scale(pbd_ee)" = "Others' behavior",                 
                         "scale(pbd_pnb)" = "What should be done", 
                         "scale(pbd_ne)" = "What others' think \nshould be done",
                         "scale(fly_ee)" = "Others' behavior",                       
                         "scale(fly_pnb)" = "What should be done", 
                         "scale(fly_ne)" = "What others' think \nshould be done",
                         "scale(politics)" = "Political orientation")) +
    xlab("Standardized coefficient estimate") + ylab("") + 
    theme_bw() +
    # Add colorblind-friendly palette & legend values = c("#000000","#D55E00","#CC79A7","#0072B2")
    scale_colour_manual(values = c("#000000","#000000","#000000","#000000", "red", "red", "red"), 
                     name = "", 
                     labels = c("Purchase an electric vehicle", "Purchase carbon offsets", "Contract for green energy", "Install solar panels", "Reduce food waste", "Eat less meat", "Fly less"),
                     guide = guide_legend(reverse = TRUE)) +
    # Add customized glyphs
    scale_shape_manual(values = c(16, 4, 15, 3, 8, 6, 0),
                      name = "",
                      labels = c("Purchase an electric vehicle", "Purchase carbon offsets", "Contract for green energy", "Install solar panels", "Reduce food waste", "Eat less meat", "Fly less"),
                      guide = guide_legend(reverse = TRUE)) +
   theme(#axis.title = element_text(size = 16),
         #plot.margin = unit(c(0,0,0,0),"cm"),
         #text = element_text(family="TT Times New Roman"),
         legend.justification = c(0, 0), 
         # Legend bottom right position 
         legend.position = c(0.66, 0.000001),
         # Legend text size
         legend.text = element_text(size = 8, colour = "black"),
         #legend.title.align = .5,
         # Transparent legend text and glyph background
         legend.background = element_rect(fill= "transparent"),
         legend.key = element_rect(colour = "transparent", fill = "transparent"),
         # Axis
         axis.line = element_line(color = "grey"),
         axis.ticks = element_line(color = "grey"),
         axis.text.x  = element_text(hjust = 1, size = 11, color = "black"),
         axis.text.y = element_text(size = 11, color = "black"),
         axis.title.x = element_text(color = "black", size = 11),
         axis.title.y = element_text(color = "black", size = 11),
         # Panel
         #panel.grid.major = element_line(size = 0.25, linetype = 'solid', color = "grey"), 
         #panel.grid.minor = element_line(size = 0.25, linetype = 'solid', color = "grey"),
         panel.background = element_blank(),
         panel.border = element_rect(color = "grey", fill = NA, size = 0.5))} %>% add_brackets(bracket, face = "bold.italic")

grid.draw(p)
ggsave("Dot-whisker.tiff", units = "in", width = 9, height = 5, device='tiff', dpi = 300)
```

##### Intention to adopt: coefficients from linear models that included demographic and psychological variables

```{r, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, fig.width = 8, fig.height = 14}
# Use tibble dfs
models <- rbind(ev_w2, offset_w2, recs_w2, solar_w2, food_waste_w2, pbd_w2, fly_less_w2)

# Create list of brackets (label, topmost included predictor, bottommost included predictor)
#bracket <- list(c("Beliefs about ...", "Others' behavior", "What others' think \nshould be done"))

p <- {dwplot(models, 
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2), 
        # Customize the of appearance of the dots and whiskers
        dot_args = list(aes(shape = model)),
        whisker_args = list(aes(linetype = model))) %>%
    # Put models on one graph by assigning them to the same names
    relabel_predictors(c("scale(ev_ee)" = "Beliefs about \nothers' behavior",                  
                         "scale(ev_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(ev_ne)" = "Beliefs about \nwhat others' think \nshould be done", 
                         "scale(offset_ee)" = "Beliefs about \nothers' behavior",            
                         "scale(offset_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(offset_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(recs_ee)" = "Beliefs about \nothers' behavior",                 
                         "scale(recs_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(recs_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(solar_ee)" = "Beliefs about \nothers' behavior",                       
                         "scale(solar_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(solar_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(foodwaste_ee)" = "Beliefs about \nothers' behavior",            
                         "scale(foodwaste_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(foodwaste_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(pbd_ee)" = "Beliefs about \nothers' behavior",                 
                         "scale(pbd_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(pbd_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(fly_ee)" = "Beliefs about \nothers' behavior",                       
                         "scale(fly_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(fly_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "sexMale" = "Gender: Male",
                         "age_group18-24" = "Age: 18-24",
                         "age_group25-34" = "Age: 25-34",
                         "age_group35-44" = "Age: 35-44",
                         "age_group45-54" = "Age: 45-54",
                         "age_group55-64" = "Age: 55-64",
                         "ethnicityAsian" = "Ethnicity: Asian",
                         "ethnicityBlack" = "Ethnicity: Black or \nAfrican American",
                         "ethnicityOther" = "Ethnicity: Other",
                         "income_category$30,000 to $49,000" = "Household income: \n$30,000 to $49,000",
                         "income_category$50,000 to $69,000" = "Household income: \n$50,000 to $69,000",
                         "income_category$70,000 to $89,000" = "Household income: \n$70,000 to $89,000",
                         "income_category$90,000 to $149,000" = "Household income: \n$90,000 to $149,000",
                         "income_category$150,000 or more" = "Household income: \n$150,000 or more",
                         "education_categoryCollege degree" = "Education level: \nCollege degree",
                         "education_categoryGraduate degree" = "Education level: \nGraduate degree",
                         "scale(politics)" = "Political orientation")) +
    xlab("Standardized coefficient estimate") + ylab("") + 
    theme_bw() +
    # Add colorblind-friendly palette & legend values = c("#000000","#D55E00","#CC79A7","#0072B2")
    scale_colour_manual(values = c("#000000","#000000","#000000","#000000", "red", "red", "red"), 
                     name = "", 
                     labels = c("Purchase an EV", "Purchase offsets", "Contract for green \nenergy", "Install solar", "Reduce food waste", "Eat less meat", "Fly less"),
                     guide = guide_legend(reverse = TRUE)) +
    # Add customized glyphs
    scale_shape_manual(values = c(16, 4, 15, 3, 8, 6, 0),
                      name = "",
                      labels = c("Purchase an EV", "Purchase offsets", "Contract for green \nenergy", "Install solar", "Reduce food waste", "Eat less meat", "Fly less"),
                      guide = guide_legend(reverse = TRUE)) +
   theme(#axis.title = element_text(size = 16),
         #plot.margin = unit(c(0,0,0,0),"cm"),
         #text = element_text(family="TT Times New Roman"),
         legend.justification = c(0, 0), 
         # Legend bottom right position 
         legend.position = c(0.77, 0.000001),
         # Legend text size
         legend.text = element_text(size = 8, colour = "black"),
         #legend.title.align = .5,
         # Transparent legend text and glyph background
         legend.background = element_rect(fill= "transparent"),
         legend.key = element_rect(colour = "transparent", fill = "transparent"),
         # Axis
         axis.line = element_line(color = "grey"),
         axis.ticks = element_line(color = "grey"),
         axis.text.x  = element_text(hjust = 1, size = 11, color = "black"),
         axis.text.y = element_text(size = 11, color = "black"),
         axis.title.x = element_text(color = "black", size = 11),
         axis.title.y = element_text(color = "black", size = 11),
         # Panel
         #panel.grid.major = element_line(size = 0.25, linetype = 'solid', color = "grey"), 
         #panel.grid.minor = element_line(size = 0.25, linetype = 'solid', color = "grey"),
         panel.background = element_blank(),
         panel.border = element_rect(color = "grey", fill = NA, size = 0.5))} #%>% add_brackets(bracket, face = "bold.italic")

grid.draw(p)
#ggsave("Dot-whisker.tiff", units = "in", width = 11, height = 6, device='tiff', dpi = 300)
```

##### Intention to adopt: coefficients from linear models that included demographic variables and political orientation only

```{r, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, fig.width = 8, fig.height = 12}
# Use tibble dfs
models <- rbind(ev_d_w, offset_d_w, recs_d_w, solar_d_w, food_waste_d_w, pbd_d_w, fly_less_d_w)

# Create list of brackets (label, topmost included predictor, bottommost included predictor)
#bracket <- list(c("Beliefs about ...", "Others' behavior", "What others' think \nshould be done"))

p <- {dwplot(models, 
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2), 
        # Customize the of appearance of the dots and whiskers
        dot_args = list(aes(shape = model)),
        whisker_args = list(aes(linetype = model))) %>%
    # Put models on one graph by assigning them to the same names
    relabel_predictors(c("sexMale" = "Gender: Male",
                         "age_group18-24" = "Age: 18-24",
                         "age_group25-34" = "Age: 25-34",
                         "age_group35-44" = "Age: 35-44",
                         "age_group45-54" = "Age: 45-54",
                         "age_group55-64" = "Age: 55-64",
                         "ethnicityAsian" = "Ethnicity: Asian",
                         "ethnicityBlack" = "Ethnicity: Black or \nAfrican American",
                         "ethnicityOther" = "Ethnicity: Other",
                         "income_category$30,000 to $49,000" = "Household income: \n$30,000 to $49,000",
                         "income_category$50,000 to $69,000" = "Household income: \n$50,000 to $69,000",
                         "income_category$70,000 to $89,000" = "Household income: \n$70,000 to $89,000",
                         "income_category$90,000 to $149,000" = "Household income: \n$90,000 to $149,000",
                         "income_category$150,000 or more" = "Household income: \n$150,000 or more",
                         "education_categoryCollege degree" = "Education level: \nCollege degree",
                         "education_categoryGraduate degree" = "Education level: \nGraduate degree",
                         "scale(politics)" = "Political orientation")) +
    xlab("Standardized coefficient estimate") + ylab("") + 
    theme_bw() +
    # Add colorblind-friendly palette & legend values = c("#000000","#D55E00","#CC79A7","#0072B2")
    scale_colour_manual(values = c("#000000","#000000","#000000","#000000", "red", "red", "red"), 
                     name = "", 
                     labels = c("Purchase an EV", "Purchase offsets", "Contract for green energy", "Install solar", "Reduce food waste", "Eat less meat", "Fly less"),
                     guide = guide_legend(reverse = TRUE)) +
    # Add customized glyphs
    scale_shape_manual(values = c(16, 4, 15, 3, 8, 6, 0),
                      name = "",
                      labels = c("Purchase an EV", "Purchase offsets", "Contract for green energy", "Install solar", "Reduce food waste", "Eat less meat", "Fly less"),
                      guide = guide_legend(reverse = TRUE)) +
   theme(#axis.title = element_text(size = 16),
         #plot.margin = unit(c(0,0,0,0),"cm"),
         #text = element_text(family="TT Times New Roman"),
         legend.justification = c(0, 0), 
         # Legend bottom right position 
         legend.position = c(0.71, 0.000001),
         # Legend text size
         legend.text = element_text(size = 8, colour = "black"),
         #legend.title.align = .5,
         # Transparent legend text and glyph background
         legend.background = element_rect(fill= "transparent"),
         legend.key = element_rect(colour = "transparent", fill = "transparent"),
         # Axis
         axis.line = element_line(color = "grey"),
         axis.ticks = element_line(color = "grey"),
         axis.text.x  = element_text(hjust = 1, size = 11, color = "black"),
         axis.text.y = element_text(size = 11, color = "black"),
         axis.title.x = element_text(color = "black", size = 11),
         axis.title.y = element_text(color = "black", size = 11),
         # Panel
         #panel.grid.major = element_line(size = 0.25, linetype = 'solid', color = "grey"), 
         #panel.grid.minor = element_line(size = 0.25, linetype = 'solid', color = "grey"),
         panel.background = element_blank(),
         panel.border = element_rect(color = "grey", fill = NA, size = 0.5))}

grid.draw(p)
#ggsave("Dot-whisker.tiff", units = "in", width = 11, height = 6, device='tiff', dpi = 300)
```

##### Program interest: coefficients from linear models that included demographic and psychological variables

```{r, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, fig.width = 8, fig.height = 14}
# Use tibble dfs
models <- rbind(ev_p, offset_p, recs_p, solar_p, food_waste_p, pbd_p, fly_less_p)

# Create list of brackets (label, topmost included predictor, bottommost included predictor)
#bracket <- list(c("Beliefs about ...", "Others' behavior", "What others' think \nshould be done"))

p <- {dwplot(models, 
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2), 
        # Customize the of appearance of the dots and whiskers
        dot_args = list(aes(shape = model)),
        whisker_args = list(aes(linetype = model))) %>%
    # Put models on one graph by assigning them to the same names
    relabel_predictors(c("scale(ev_ee)" = "Beliefs about \nothers' behavior",                  
                         "scale(ev_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(ev_ne)" = "Beliefs about \nwhat others' think \nshould be done", 
                         "scale(offset_ee)" = "Beliefs about \nothers' behavior",            
                         "scale(offset_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(offset_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(recs_ee)" = "Beliefs about \nothers' behavior",                 
                         "scale(recs_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(recs_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(solar_ee)" = "Beliefs about \nothers' behavior",                       
                         "scale(solar_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(solar_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(foodwaste_ee)" = "Beliefs about \nothers' behavior",            
                         "scale(foodwaste_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(foodwaste_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(pbd_ee)" = "Beliefs about \nothers' behavior",                 
                         "scale(pbd_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(pbd_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(fly_ee)" = "Beliefs about \nothers' behavior",                       
                         "scale(fly_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(fly_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "sexMale" = "Gender: Male",
                         "age_group18-24" = "Age: 18-24",
                         "age_group25-34" = "Age: 25-34",
                         "age_group35-44" = "Age: 35-44",
                         "age_group45-54" = "Age: 45-54",
                         "age_group55-64" = "Age: 55-64",
                         "ethnicityAsian" = "Ethnicity: Asian",
                         "ethnicityBlack" = "Ethnicity: Black or \nAfrican American",
                         "ethnicityOther" = "Ethnicity: Other",
                         "income_category$30,000 to $49,000" = "Household income: \n$30,000 to $49,000",
                         "income_category$50,000 to $69,000" = "Household income: \n$50,000 to $69,000",
                         "income_category$70,000 to $89,000" = "Household income: \n$70,000 to $89,000",
                         "income_category$90,000 to $149,000" = "Household income: \n$90,000 to $149,000",
                         "income_category$150,000 or more" = "Household income: \n$150,000 or more",
                         "education_categoryCollege degree" = "Education level: \nCollege degree",
                         "education_categoryGraduate degree" = "Education level: \nGraduate degree",
                         "scale(politics)" = "Political orientation")) +
    xlab("Standardized coefficient estimate") + ylab("") + 
    theme_bw() +
    # Add colorblind-friendly palette & legend values = c("#000000","#D55E00","#CC79A7","#0072B2")
    scale_colour_manual(values = c("#000000","#000000","#000000","#000000", "red", "red", "red"), 
                     name = "", 
                     labels = c("Program interest: EV", "Program interest: offsets", "Program interest: green energy", "Program interest: solar", "Program interest: reduce food waste", "Program interest: PBD", "Program interest: Fly less"),
                     guide = guide_legend(reverse = TRUE)) +
    # Add customized glyphs
    scale_shape_manual(values = c(16, 4, 15, 3, 8, 6, 0),
                      name = "",
                      labels = c("Program interest: EV", "Program interest: offsets", "Program interest: green energy", "Program interest: solar", "Program interest: reduce food waste", "Program interest: PBD", "Program interest: Fly less"),
                      guide = guide_legend(reverse = TRUE)) +
   theme(#axis.title = element_text(size = 16),
         #plot.margin = unit(c(0,0,0,0),"cm"),
         #text = element_text(family="TT Times New Roman"),
         legend.justification = c(0, 0), 
         # Legend bottom right position 
         legend.position = c(0.01, 0.000001),
         # Legend text size
         legend.text = element_text(size = 8, colour = "black"),
         #legend.title.align = .5,
         # Transparent legend text and glyph background
         legend.background = element_rect(fill= "transparent"),
         legend.key = element_rect(colour = "transparent", fill = "transparent"),
         # Axis
         axis.line = element_line(color = "grey"),
         axis.ticks = element_line(color = "grey"),
         axis.text.x  = element_text(hjust = 1, size = 11, color = "black"),
         axis.text.y = element_text(size = 11, color = "black"),
         axis.title.x = element_text(color = "black", size = 11),
         axis.title.y = element_text(color = "black", size = 11),
         # Panel
         #panel.grid.major = element_line(size = 0.25, linetype = 'solid', color = "grey"), 
         #panel.grid.minor = element_line(size = 0.25, linetype = 'solid', color = "grey"),
         panel.background = element_blank(),
         panel.border = element_rect(color = "grey", fill = NA, size = 0.5))} #%>% add_brackets(bracket, face = "bold.italic")

grid.draw(p)
#ggsave("Dot-whisker.tiff", units = "in", width = 11, height = 6, device='tiff', dpi = 300)
```

##### Program interest: coefficients from linear models that included demographic variables and political orientation only

```{r, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE, fig.width = 8, fig.height = 14}
# Use tibble dfs
models <- rbind(ev_p_d, offset_p_d, recs_p_d, solar_p_d, food_waste_p_d, pbd_p_d, fly_less_p_d)

# Create list of brackets (label, topmost included predictor, bottommost included predictor)
#bracket <- list(c("Beliefs about ...", "Others' behavior", "What others' think \nshould be done"))

p <- {dwplot(models, 
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2), 
        # Customize the of appearance of the dots and whiskers
        dot_args = list(aes(shape = model)),
        whisker_args = list(aes(linetype = model))) %>%
    # Put models on one graph by assigning them to the same names
    relabel_predictors(c("scale(ev_ee)" = "Beliefs about \nothers' behavior",                  
                         "scale(ev_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(ev_ne)" = "Beliefs about \nwhat others' think \nshould be done", 
                         "scale(offset_ee)" = "Beliefs about \nothers' behavior",            
                         "scale(offset_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(offset_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(recs_ee)" = "Beliefs about \nothers' behavior",                 
                         "scale(recs_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(recs_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(solar_ee)" = "Beliefs about \nothers' behavior",                       
                         "scale(solar_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(solar_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(foodwaste_ee)" = "Beliefs about \nothers' behavior",            
                         "scale(foodwaste_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(foodwaste_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(pbd_ee)" = "Beliefs about \nothers' behavior",                 
                         "scale(pbd_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(pbd_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "scale(fly_ee)" = "Beliefs about \nothers' behavior",                       
                         "scale(fly_pnb)" = "Beliefs about \nwhat should be done", 
                         "scale(fly_ne)" = "Beliefs about \nwhat others' think \nshould be done",
                         "sexMale" = "Gender: Male",
                         "age_group18-24" = "Age: 18-24",
                         "age_group25-34" = "Age: 25-34",
                         "age_group35-44" = "Age: 35-44",
                         "age_group45-54" = "Age: 45-54",
                         "age_group55-64" = "Age: 55-64",
                         "ethnicityAsian" = "Ethnicity: Asian",
                         "ethnicityBlack" = "Ethnicity: Black or \nAfrican American",
                         "ethnicityOther" = "Ethnicity: Other",
                         "income_category$30,000 to $49,000" = "Household income: \n$30,000 to $49,000",
                         "income_category$50,000 to $69,000" = "Household income: \n$50,000 to $69,000",
                         "income_category$70,000 to $89,000" = "Household income: \n$70,000 to $89,000",
                         "income_category$90,000 to $149,000" = "Household income: \n$90,000 to $149,000",
                         "income_category$150,000 or more" = "Household income: \n$150,000 or more",
                         "education_categoryCollege degree" = "Education level: \nCollege degree",
                         "education_categoryGraduate degree" = "Education level: \nGraduate degree",
                         "scale(politics)" = "Political orientation")) +
    xlab("Standardized coefficient estimate") + ylab("") + 
    theme_bw() +
    # Add colorblind-friendly palette & legend values = c("#000000","#D55E00","#CC79A7","#0072B2")
    scale_colour_manual(values = c("#000000","#000000","#000000","#000000", "red", "red", "red"), 
                     name = "", 
                     labels = c("Program interest: EV", "Program interest: offsets", "Program interest: green energy", "Program interest: solar", "Program interest: reduce food waste", "Program interest: PBD", "Program interest: Fly less"),
                     guide = guide_legend(reverse = TRUE)) +
    # Add customized glyphs
    scale_shape_manual(values = c(16, 4, 15, 3, 8, 6, 0),
                      name = "",
                      labels = c("Program interest: EV", "Program interest: offsets", "Program interest: green energy", "Program interest: solar", "Program interest: reduce food waste", "Program interest: PBD", "Program interest: Fly less"),
                      guide = guide_legend(reverse = TRUE)) +
   theme(#axis.title = element_text(size = 16),
         #plot.margin = unit(c(0,0,0,0),"cm"),
         #text = element_text(family="TT Times New Roman"),
         legend.justification = c(0, 0), 
         # Legend bottom right position 
         legend.position = c(0.01, 0.000001),
         # Legend text size
         legend.text = element_text(size = 8, colour = "black"),
         #legend.title.align = .5,
         # Transparent legend text and glyph background
         legend.background = element_rect(fill= "transparent"),
         legend.key = element_rect(colour = "transparent", fill = "transparent"),
         # Axis
         axis.line = element_line(color = "grey"),
         axis.ticks = element_line(color = "grey"),
         axis.text.x  = element_text(hjust = 1, size = 11, color = "black"),
         axis.text.y = element_text(size = 11, color = "black"),
         axis.title.x = element_text(color = "black", size = 11),
         axis.title.y = element_text(color = "black", size = 11),
         # Panel
         #panel.grid.major = element_line(size = 0.25, linetype = 'solid', color = "grey"), 
         #panel.grid.minor = element_line(size = 0.25, linetype = 'solid', color = "grey"),
         panel.background = element_blank(),
         panel.border = element_rect(color = "grey", fill = NA, size = 0.5))} #%>% add_brackets(bracket, face = "bold.italic")

grid.draw(p)
#ggsave("Dot-whisker.tiff", units = "in", width = 11, height = 6, device='tiff', dpi = 300)
```

#### People underestimate how many people think they should take actions

```{r, echo = FALSE, results = 'asis', message = FALSE, warning = FALSE}
pnb_ne_plot <- data %>% 
  select(
  #wt,
  #Vrid,
  #var13, #RID
  #EV
  #var26, #adoption
  #var87, #EE
  var28, #PNB,
  var88, #NE
  #var94, #intent
  #var96, #program interest
  #Fly
  #var70, #Are you trying to fly less frequently than you used to?
  #var69, #EE
  var38, #PNB
  var35, #NE
  #var97, #intent
  #var98, #program interest
  #Offsets
  #var39, #adoption
  #var40, #EE
  var41, #PNB
  var42, #NE
  #var99, #intent
  #var100, #program interest
  #PBD
  #var71, #Are you trying to eat less meat than you used to?
  #var115, #adoption % of meals
  #var72, #EE
  var66, #PNB
  var48, #NE
  #var103, #intent
  #var104, #program interest
  #RECs
  #var54, #adoption
  #var55, #EE
  var56, #PNB
  var57, #NE
  #var105, #intent
  #var106, #program interest
  #Solar
  #var59, #adoption
  #var60, #EE
  var61, #PNB
  var62, #NE
  #var107, #intent
  #var108, #program interest
  #Food waste
  #var73, #Are you currently trying to reduce the amount of food waste you produce?
  #var74, #EE
  var75, #PNB
  var76, #NE
  #var109, #intent
  #var110, #program interest
  #demographics
  #age_group,
  #sex,
  #ethnicity,
  #var20, #politics
  #var19, #income
  #var17, #education
  ) %>% 
  rename(
  #EV
  #ev_adoption = var26,
  #ev_ee = var87,
  ev_pnb = var28,
  ev_ne = var88,
  #ev_intent = var94,
  #ev_program_interest = var96,
  #Fly
  #fly_adoption = var70, #trying to fly less
  #fly_ee = var69, #EE
  fly_pnb = var38, #PNB
  fly_ne = var35, #NE
  #fly_intent = var97,
  #fly_program_interest = var98,
  #Offset
  #offset_adoption = var39, #adoption
  #offset_ee = var40, #EE
  offset_pnb = var41, #PNB
  offset_ne = var42, #NE
  #offset_program_interest = var100, #program interest
  #offset_intent = var99,
  #PBD
  #pbd_adoption = var71, #trying to
  #pbd_ee = var72, #EE
  pbd_pnb = var66, #PNB
  pbd_ne = var48, #NE
  #pbd_program_interest = var104, #program interest
  #pbd_intent = var103, 
  #RECs
  #recs_adoption = var54, #adoption
  #recs_ee = var55, #EE
  recs_pnb = var56, #PNB
  recs_ne = var57, #NE
  #recs_program_interest = var106, #program interest
  #recs_intent = var105,
  #Solar
  #solar_adoption = var59, #adoption
  #solar_ee = var60, #EE
  solar_pnb = var61, #PNB
  solar_ne = var62, #NE
  #solar_program_interest = var108, #program interest
  #solar_intent = var107,
  #Food waste
  #foodwaste_adoption = var73, #attempt
  #foodwaste_ee = var74, #EE
  foodwaste_pnb = var75, #PNB
  foodwaste_ne = var76, #NE
  #foodwaste_program_interest = var110, #program interest
  #foodwaste_intent = var109
  )

avgNE = pnb_ne_plot %>%
  select(ev_ne, offset_ne, pbd_ne, fly_ne, solar_ne, recs_ne, foodwaste_ne) %>%
  summarise_all(mean) %>%
  gather() %>%
  mutate(
    value = value*10,
    key = recode(key, ev_ne = "Next car \nis EV", offset_ne = "Buy offsets", pbd_ne = "Eat less \nmeat", fly_ne = "Fly less", recs_ne = "Buy green \nenergy", solar_ne = "Install solar", foodwaste_ne = "Reduce food \nwaste"))


avgPNB = pnb_ne_plot %>%
  select(ev_pnb, offset_pnb, pbd_pnb, fly_pnb, solar_pnb, recs_pnb, foodwaste_pnb)%>%
  summarise_all(mean)%>%
  gather()%>%
  mutate(
    value = value*100,
    key = recode(key, ev_pnb = "Next car \nis EV", offset_pnb = "Buy offsets", pbd_pnb = "Eat less \nmeat", fly_pnb = "Fly less", recs_pnb = "Buy green \nenergy", solar_pnb = "Install solar", foodwaste_pnb = "Reduce food \nwaste"))

normativediff = full_join(avgPNB, avgNE, by = "key") %>%
  arrange(value.x) %>%
  rename("Perceived proportion\nthinking people should" = value.y, "Actual proportion\nthinking people should" = value.x) %>% 
  mutate(
    
  )

normativediff %>%
gather("belief", "Prevalence", -key)%>%
  ggplot(aes(x = reorder(key, -Prevalence),y = Prevalence, fill = belief))+
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#005BBB", "grey"),
                    name = "Beliefs", labels = c("Actual % thinking people should \nadopt the behaviors", "Perceived % thinking people \nshould adopt the behaviors")) +
theme(axis.line = element_line(color="white"),
        axis.ticks = element_line(color="white"),
        panel.border = element_blank(),
        axis.title.y = element_text(color = "black", size = 10.5),
        axis.title.x = element_blank(),
        axis.text.x = element_text(colour="black", size = 10.5),
        axis.text.y = element_text(colour="black", size = 10.5),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.position = "bottom") +
  scale_y_continuous(labels = function(x) paste0(x,"%"))
```